### 2025-04-22 docs/tex_src/main.tex
project template

\documentclass[a4paper,10pt]{article}
\usepackage[utf8]{inputenc}
\newcommand{\myparagraph}[1]{\paragraph{#1}\mbox{}\\}
\usepackage[a4paper,margin=3.5cm]{geometry} %Sets the page geometry
\usepackage{url}
\usepackage{dirtytalk}
\usepackage{graphicx} % Package for \includegraphics
\usepackage{wrapfig} % Figure wrapping
\usepackage[T1]{fontenc} % Output font encoding for international characters
\setlength{\parskip}{1em} % Set space when paragraphs are used
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{tcolorbox}
\usepackage{mathtools}
\usepackage{enumerate}

% Lets you use \blankpage to make a blank page
\newcommand{\blankpage}{
	\newpage
	\thispagestyle{empty}
	\mbox{}
	\newpage
}

% Self Explanatory
\newtheorem{theorem}{Theorem}[section]
\newtheorem{definition}{Definition}[section]
\newtheorem{corollary}{Corollary}[theorem]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{example}{Example}[section]
\newtheorem{proof}{Proof}[section]

% Other
\DeclarePairedDelimiter\floor{\lfloor}{\rfloor} %Floor function

### 2025-04-24 docs/tex_src/main.tex
notes

@@
 \newcommand{\myparagraph}[1]{\paragraph{#1}\mbox{}\\}
-\usepackage[a4paper,margin=3.5cm]{geometry} %Sets the page geometry
+\usepackage[a4paper,margin=1.5cm]{geometry} %Sets the page geometry
 \usepackage{url}
@@
 \usepackage{enumerate}
+\usepackage{algorithm}
+\usepackage{algorithmicx}
+\usepackage{algpseudocode}
 
@@
 \DeclarePairedDelimiter\floor{\lfloor}{\rfloor} %Floor function
+
+\begin{document}
+\begin{flushleft}
+	\section{P2P Network Design}
+	\begin{itemize}
+		\item $N$ - nodes in network
+		\item $L$ - layers in model
+		\item $l_i = (x,y) : x,y \in [0,L); y > x$ - range of layers node $i$ has
+		\item $\ell _{ij}$ - latency from node $i$ to node $j$
+		\item $c_i$ - computational cost of node $i$
+		\item $p_i$ - preload cost of node $i$
+		\item $e_i$ - embedding cost of node $i$
+	\end{itemize}
+
+	\section{Optimal Path Finding}
+	The P2P network is constructed as a directed graph. Edges are compatiable nodes with the next layers of the model.
+	We know that this is a DAG becasue the layers must be preformed sequentially. The weights of the edges are the sum of latency and computational cost.
+	The optimal path can be found using a topological sort. The start node is the users computer, and the terminal nodes are all nodes that have layer N.
+	The optimal path connects the start node to a terminal node.
+
+	\subsection{Topological Sort}
+	\begin{algorithm}
+		\caption{Topological Sort of a Directed Acyclic Graph (DAG)}
+		\begin{algorithmic}[1]
+			\Require{A directed acyclic graph $G = (V, E)$}
+			\Ensure{A linear ordering of vertices such that for every directed edge $(u, v)$, vertex $u$ comes before vertex $v$}
+
+			\State $\text{result}[]$ \Comment An empty list to store the sorted vertices
+			\State $\text{visited}[\text{false}; V]$ \Comment A map to track visited vertices
+			\State $\text{temp}[\text{false}; V]$ \Comment A map to track vertices in the current recursion stack
+
+			\For{each vertex $v \in V$}
+			\If{$\text{visited}[v] = \text{false}$}
+			\State DFS-Visit($G$, $v$, $\text{visited}$, $\text{temp}$, $\text{result}$)
+			\EndIf
+			\EndFor
+
+			\State \Return Reverse($\text{result}$)
+
+			\Function{DFS-Visit}{$G$, $u$, $\text{visited}$, $\text{temp}$, $\text{result}$}
+			\State $\text{temp}[u] \gets \text{true}$ \Comment{Mark current vertex as being processed}
+
+			\For{each vertex $v$ such that $(u, v) \in E$}
+			\State DFS-Visit($G$, $v$, $\text{visited}$, $\text{temp}$, $\text{result}$)
+			\EndFor
+
+			\State $\text{temp}[u] \gets \text{false}$ \Comment{Mark $u$ as processed}
+			\State $\text{visited}[u] \gets \text{true}$ \Comment{Mark $u$ as visited}
+			\State Append $u$ to $\text{result}$
+			\EndFunction
+		\end{algorithmic}
+	\end{algorithm}
+	\subsection{Dynamic Programming}
+\end{flushleft}
+\end{document}

### 2025-04-25 src/backend/graph.rs
backend module

@@ -1,0 +1,67 @@
+use std::collections::{HashMap, HashSet};
+
+/// A directed graph implementation using adjacency lists
+pub struct DirectedGraph<T>
+where
+    T: Eq + std::hash::Hash + Clone,
+{
+    /// Maps each node to its set of outgoing edges
+    adjacency_list: HashMap<T, HashSet<T>>,
+}
+
+impl<T> DirectedGraph<T>
+where
+    T: Eq + std::hash::Hash + Clone,
+{
+    /// Creates a new empty directed graph
+    pub fn new() -> Self {
+        DirectedGraph {
+            adjacency_list: HashMap::new(),
+        }
+    }
+
+    /// Adds a node to the graph if it doesn't already exist
+    pub fn add_node(&mut self, node: T) {
+        self.adjacency_list.entry(node).or_insert_with(HashSet::new);
+    }
+
+    /// Adds a directed edge from source to destination
+    /// If the nodes don't exist yet, they are automatically added
+    pub fn add_edge(&mut self, source: T, destination: T) {
+        // Add source and destination nodes if they don't exist
+        self.add_node(source.clone());
+        self.add_node(destination.clone());
+
+        // Add the edge
+        self.adjacency_list
+            .get_mut(&source)
+            .unwrap()
+            .insert(destination);
+    }
+
+    /// Returns true if the graph contains the node
+    pub fn has_node(&self, node: &T) -> bool {
+        self.adjacency_list.contains_key(node)
+    }
+
+    /// Returns true if there is a direct edge from source to destination
+    pub fn has_edge(&self, source: &T, destination: &T) -> bool {
+        match self.adjacency_list.get(source) {
+            Some(neighbors) => neighbors.contains(destination),
+            None => false,
+        }
+    }
+
+    /// Returns a vector of all nodes in the graph
+    pub fn nodes(&self) -> Vec<T> {
+        self.adjacency_list.keys().cloned().collect()
+    }
+
+    /// Returns a vector of all neighbors of a node
+    pub fn neighbors(&self, node: &T) -> Vec<T> {
+        match self.adjacency_list.get(node) {
+            Some(neighbors) => neighbors.iter().cloned().collect(),
+            None => Vec::new(),
+        }
+    }
+}

### 2025-04-25 src/backend/mod.rs

@@ -1,0 +1,2 @@
+pub mod graph;
+pub mod p2p;

### 2025-04-25 src/backend/p2p.rs

@@ -1,0 +1,154 @@
+use std::collections::HashMap;
+use std::hash::{Hash, Hasher};
+
+use super::graph;
+
+// Given a vec of Nodes in P2P network, create a directed graph
+// Directions in the graph represent compatibility between layer ranges
+//
+// # Arguments
+//
+// * `nodes` - Vec of nodes in network
+//
+// # Returns
+//
+//  Verticies and edges of graph
+pub fn make_graph(nodes: &Vec<P2PNode>) -> graph::DirectedGraph<&P2PNode> {
+    let mut graph = graph::DirectedGraph::new();
+
+    // Add all nodes to vertices
+    for node in nodes {
+        graph.add_node(node);
+    }
+
+    // Create edges based on layer range compatibility
+    for source_node in nodes {
+        for target_node in nodes {
+            // Skip self loops
+            if source_node.id == target_node.id {
+                continue;
+            }
+
+            // Create an edge if target node's layer range is one greater than source node's
+            if target_node.params.layer_range == source_node.params.layer_range + 1 {
+                graph.add_edge(source_node, target_node);
+            }
+        }
+    }
+
+    graph
+}
+
+#[derive(Clone, PartialEq, Eq, Debug)]
+pub struct P2PNode {
+    pub id: usize,
+    pub params: NodeParameters,
+}
+
+impl P2PNode {
+    /// Creates a new P2PNode with the given id and parameters.
+    ///
+    /// # Arguments
+    ///
+    /// * `id` - A unique identifier for this node
+    /// * `params` - The parameters that configure this node's behavior
+    ///
+    /// # Returns
+    ///
+    /// A new P2PNode instance
+    pub fn new(id: usize, params: NodeParameters) -> Self {
+        P2PNode { id, params }
+    }
+}
+
+/// Implements the Hash trait for P2PNode.
+///
+/// This implementation only hashes the `id` field, ignoring the `params` field.
+/// This means two P2PNodes with the same id will hash to the same value,
+/// regardless of their parameters.
+impl Hash for P2PNode {
+    fn hash<H: Hasher>(&self, state: &mut H) {
+        self.id.hash(state);
+    }
+}
+
+// Represents the parameters for a node in a distributed system.
+///
+/// # Fields
+///
+/// * `layer_range` - Range of layers node i has
+/// * `latencies` - Map of latencies from this node to other nodes, where the key is the node ID
+/// * `computational_cost` - Computational cost of the node
[…]

### 2025-04-25 src/main.rs

@@ -1,3 +1,8 @@
+mod backend;
+
+// import p2p network
+use backend::p2p;
+
 fn main() {
     println!("Hello, world!");
 }

### 2025-04-25 src/backend/graph.rs
topo sort

@@ -39,19 +39,6 @@ where
             .insert(destination);
     }
 
-    /// Returns true if the graph contains the node
-    pub fn has_node(&self, node: &T) -> bool {
-        self.adjacency_list.contains_key(node)
-    }
-
-    /// Returns true if there is a direct edge from source to destination
-    pub fn has_edge(&self, source: &T, destination: &T) -> bool {
-        match self.adjacency_list.get(source) {
-            Some(neighbors) => neighbors.contains(destination),
-            None => false,
-        }
-    }
-
     /// Returns a vector of all nodes in the graph
     pub fn nodes(&self) -> Vec<T> {
         self.adjacency_list.keys().cloned().collect()
@@ -63,5 +50,64 @@ where
             Some(neighbors) => neighbors.iter().cloned().collect(),
             None => Vec::new(),
         }
+    }
+
+    /// Performs a topological sort of the graph
+    /// Returns a Result containing either:
+    /// - Ok(Vec<T>): A topologically sorted vector of nodes
+    /// - Err(String): An error message if the graph is not a DAG (contains cycles)
+    pub fn topological_sort(&self) -> Result<Vec<T>, String> {
+        // Track visited nodes and recursion stack to detect cycles
+        let mut visited = HashSet::new();
+        let mut rec_stack = HashSet::new();
+        let mut result = Vec::new();
+
+        // Define a recursive DFS function for topological sort
+        fn dfs<T: Eq + std::hash::Hash + Clone>(
+            graph: &DirectedGraph<T>,
+            node: &T,
+            visited: &mut HashSet<T>,
+            rec_stack: &mut HashSet<T>,
+            result: &mut Vec<T>,
+        ) -> Result<(), String> {
+            // Mark the current node as visited and add to recursion stack
+            visited.insert(node.clone());
+            rec_stack.insert(node.clone());
+
+            // Visit all neighbors
+            for neighbor in graph.neighbors(node) {
+                // If neighbor is in recursion stack, we found a cycle
+                if rec_stack.contains(&neighbor) {
+                    return Err(format!("Graph contains a cycle"));
+                }
+
+                // If not visited, recursively visit
+                if !visited.contains(&neighbor) {
+                    if let Err(e) = dfs(graph, &neighbor, visited, rec_stack, result) {
+                        return Err(e);
+                    }
+                }
+            }
+
+            // Remove the node from recursion stack and add it to result
+            rec_stack.remove(node);
+            result.push(node.clone());
+
[…]

### 2025-04-25 src/backend/p2p.rs

@@ -119,14 +119,14 @@ impl NodeParameters {
         computational_cost: u32,
         preload_cost: u32,
         embedding_cost: u32,
-    ) -> Result<Self, &'static str> {
-        Ok(NodeParameters {
+    ) -> Self {
+        NodeParameters {
             layer_range,
             latencies: HashMap::new(),
             computational_cost,
             preload_cost,
             embedding_cost,
-        })
+        }
     }
 
     /// Sets the latency from this node to another node

### 2025-04-25 src/main.rs

@@ -1,8 +1,41 @@
 mod backend;
 
 // import p2p network
-use backend::p2p;
+use backend::graph::DirectedGraph;
+use backend::p2p::{make_graph, NodeParameters, P2PNode};
 
 fn main() {
-    println!("Hello, world!");
+    let node_params_0 = NodeParameters::new(0, 1, 1, 1);
+    let node_params_1 = NodeParameters::new(1, 1, 1, 1);
+    let node_params_2 = NodeParameters::new(2, 1, 1, 1);
+    let node_params_3 = NodeParameters::new(3, 1, 1, 1);
+
+    let node0 = P2PNode::new(0, node_params_0);
+    let node1 = P2PNode::new(1, node_params_1);
+    let node2 = P2PNode::new(2, node_params_2);
+    let node3 = P2PNode::new(3, node_params_3);
+
+    let nodes = vec![node0, node1, node2, node3];
+
+    let graph = make_graph(&nodes);
+
+    let nodes_in_graph = DirectedGraph::nodes(&graph);
+
+    for node in nodes_in_graph {
+        let neighbors = DirectedGraph::neighbors(&graph, &node);
+        println!("Node ID: {} Layer: {}", node.id, node.params.layer_range);
+        for n in neighbors {
+            println!("Neighbor {}", n.id);
+        }
+    }
+
+    let sorted_nodes = match DirectedGraph::topological_sort(&graph) {
+        Ok(nodes) => nodes,
+        Err(e) => panic!("Error sorting nodes: {}", e),
+    };
+
+    println!("Sorted Nodes");
+    for node in sorted_nodes {
+        println!("{}", node.id);
+    }
 }

### 2025-04-26 src/backend/p2p.rs
add P2PNetwork

@@ -3,40 +3,182 @@ use std::hash::{Hash, Hasher};
 
 use super::graph;
 
-// Given a vec of Nodes in P2P network, create a directed graph
-// Directions in the graph represent compatibility between layer ranges
-//
-// # Arguments
-//
-// * `nodes` - Vec of nodes in network
-//
-// # Returns
-//
-//  Verticies and edges of graph
-pub fn make_graph(nodes: &Vec<P2PNode>) -> graph::DirectedGraph<&P2PNode> {
-    let mut graph = graph::DirectedGraph::new();
+/// Represents a peer-to-peer network composed of nodes with specific layer ranges
+/// and connectivity information.
+///
+/// # Fields
+///
+/// * `nodes` - All nodes in the network
+/// * `start_node_ids` - IDs of nodes that serve as entry points to the network (at min_layer)
+/// * `end_node_ids` - IDs of nodes that serve as terminal points in the network (at max_layer)
+/// * `min_layer` - The minimum layer range in the network
+/// * `max_layer` - The maximum layer range in the network
+pub struct P2PNetwork {
+    pub nodes: Vec<P2PNode>,
+    pub start_node_ids: Vec<usize>,
+    pub end_node_ids: Vec<usize>,
+    pub min_layer: u8,
+    pub max_layer: u8,
+}
 
-    // Add all nodes to vertices
-    for node in nodes {
-        graph.add_node(node);
-    }
-
-    // Create edges based on layer range compatibility
-    for source_node in nodes {
-        for target_node in nodes {
-            // Skip self loops
-            if source_node.id == target_node.id {
-                continue;
-            }
-
-            // Create an edge if target node's layer range is one greater than source node's
-            if target_node.params.layer_range == source_node.params.layer_range + 1 {
-                graph.add_edge(source_node, target_node);
-            }
+impl P2PNetwork {
+    /// Creates a new P2PNetwork with empty node vectors and default layer bounds.
+    ///
+    /// # Returns
+    ///
+    /// A new P2PNetwork instance with empty node collections and u8::MAX/u8::MIN as initial bounds
+    pub fn new() -> Self {
+        P2PNetwork {
+            nodes: Vec::new(),
+            start_node_ids: Vec::new(),
+            end_node_ids: Vec::new(),
+            min_layer: u8::MAX,
+            max_layer: u8::MIN,
         }
     }
 
-    graph
+    /// Creates a new P2PNetwork from a list of nodes, automatically determining
[…]

### 2025-04-26 src/main.rs

@@ -2,13 +2,18 @@ mod backend;
 
 // import p2p network
 use backend::graph::DirectedGraph;
-use backend::p2p::{make_graph, NodeParameters, P2PNode};
+use backend::p2p::{NodeParameters, P2PNetwork, P2PNode};
 
 fn main() {
-    let node_params_0 = NodeParameters::new(0, 1, 1, 1);
-    let node_params_1 = NodeParameters::new(1, 1, 1, 1);
-    let node_params_2 = NodeParameters::new(2, 1, 1, 1);
-    let node_params_3 = NodeParameters::new(3, 1, 1, 1);
+    let mut node_params_0 = NodeParameters::new(0, 1, 1, 1);
+    let mut node_params_1 = NodeParameters::new(1, 1, 1, 1);
+    let mut node_params_2 = NodeParameters::new(2, 1, 1, 1);
+    let mut node_params_3 = NodeParameters::new(3, 1, 1, 1);
+
+    NodeParameters::set_latency(&mut node_params_0, 1, 5);
+    NodeParameters::set_latency(&mut node_params_1, 1, 9);
+    NodeParameters::set_latency(&mut node_params_2, 1, 2);
+    NodeParameters::set_latency(&mut node_params_3, 1, 7);
 
     let node0 = P2PNode::new(0, node_params_0);
     let node1 = P2PNode::new(1, node_params_1);
@@ -17,7 +22,24 @@ fn main() {
 
     let nodes = vec![node0, node1, node2, node3];
 
-    let graph = make_graph(&nodes);
+    let network = P2PNetwork::from_nodes(nodes);
+
+    let graph = P2PNetwork::make_graph(&network);
+
+    println!(
+        "Min Layer: {} Make Layer: {}",
+        network.min_layer, network.max_layer
+    );
+
+    let min_nodes = P2PNetwork::start_nodes(&network);
+
+    for node in min_nodes {
+        println!("Start Node: {}", node.id);
+    }
+    let max_nodes = P2PNetwork::end_nodes(&network);
+    for node in max_nodes {
+        println!("End Node: {}", node.id);
+    }
 
     let nodes_in_graph = DirectedGraph::nodes(&graph);
 
@@ -36,6 +58,7 @@ fn main() {
 
     println!("Sorted Nodes");
     for node in sorted_nodes {
-        println!("{}", node.id);
+        let l = NodeParameters::get_latency(&node.params, &1).expect("latency not defined");
+        println!("Node ID: {} Latency to 1: {}", node.id, l);
     }
 }

### 2025-04-26 src/backend/p2p.rs
add fn to update layer range

@@ -109,6 +109,33 @@ impl P2PNetwork {
         self.nodes.push(node);
     }
 
+    // Changes a nodes layer range in the network, automatically updating start_node_ids,
+    // end_node_ids if needed
+    //
+    // # Arguments
+    //
+    // * `node` - The node to change in the network
+    // * `new_layer` - The new layer range to set
+    pub fn change_node_layer(&mut self, node: &mut P2PNode, new_layer: u8) {
+        let node_id = node.id;
+        let current_layer = node.params.layer_range;
+        node.params.layer_range = new_layer;
+
+        // Remove node if previously was start or end
+        if current_layer == self.min_layer {
+            self.start_node_ids.retain(|id| *id != node_id);
+        } else if current_layer == self.max_layer {
+            self.end_node_ids.retain(|id| *id != node_id);
+        }
+
+        // Add to aprropriate list if new range is start or end
+        if new_layer == self.min_layer {
+            self.start_node_ids.push(node_id);
+        } else if new_layer == self.max_layer {
+            self.end_node_ids.push(node_id);
+        }
+    }
+
     /// Given the current nodes in the P2P network, create a directed graph.
     /// Directions in the graph represent compatibility between layer ranges,
     /// where an edge exists if the target node's layer range is one greater than
@@ -185,6 +212,7 @@ impl P2PNetwork {
 pub struct P2PNode {
     pub id: usize,
     pub params: NodeParameters,
+    pub queue: Vec<u32>,
 }
 
 impl P2PNode {
@@ -199,7 +227,11 @@ impl P2PNode {
     ///
     /// A new P2PNode instance
     pub fn new(id: usize, params: NodeParameters) -> Self {
-        P2PNode { id, params }
+        P2PNode {
+            id,
+            params,
+            queue: Vec::new(),
+        }
     }
 }
 

### 2025-04-26 src/backend/p2p.rs
add contracts

@@ -1,4 +1,4 @@
-use std::collections::HashMap;
+use std::collections::{HashMap, VecDeque};
 use std::hash::{Hash, Hasher};
 
 use super::graph;
@@ -13,15 +13,16 @@ use super::graph;
 /// * `end_node_ids` - IDs of nodes that serve as terminal points in the network (at max_layer)
 /// * `min_layer` - The minimum layer range in the network
 /// * `max_layer` - The maximum layer range in the network
-pub struct P2PNetwork {
+pub struct P2PNetwork<'a> {
     pub nodes: Vec<P2PNode>,
     pub start_node_ids: Vec<usize>,
     pub end_node_ids: Vec<usize>,
     pub min_layer: u8,
     pub max_layer: u8,
+    pub contracts: Vec<Contract<'a>>,
 }
 
-impl P2PNetwork {
+impl<'a> P2PNetwork<'a> {
     /// Creates a new P2PNetwork with empty node vectors and default layer bounds.
     ///
     /// # Returns
@@ -34,6 +35,7 @@ impl P2PNetwork {
             end_node_ids: Vec::new(),
             min_layer: u8::MAX,
             max_layer: u8::MIN,
+            contracts: Vec::new(),
         }
     }
 
@@ -74,6 +76,7 @@ impl P2PNetwork {
             end_node_ids,
             min_layer,
             max_layer,
+            contracts: Vec::new(),
         }
     }
 
@@ -208,11 +211,174 @@ impl P2PNetwork {
     }
 }
 
+/// Represents a sub-contract within a larger contract system
+///
+/// A `SubContract` defines a relationship between a source and destination entity
+/// with a time constraint for completion.
+#[derive(Clone, PartialEq, Eq, Debug)]
+pub struct SubContract {
+    /// Identifier for the source entity
+    pub source_id: u8,
+
+    /// Identifier for the destination entity
+    pub dest_id: u8,
+
+    /// Time remaining (in seconds) before the sub-contract expires
+    pub time_left: u32,
+}
+
+impl SubContract {
+    /// Creates a new sub-contract
+    ///
+    /// # Arguments
+    ///
+    /// * `source_id` - The ID of the source entity
+    /// * `dest_id` - The ID of the destination entity
+    /// * `time_left` - Time until expiration in seconds
+    ///
+    /// # Returns
+    ///
+    /// A new `SubContract` instance
+    pub fn new(source_id: u8, dest_id: u8, time_left: u32) -> Self {
[…]

### 2025-04-27 src/backend/p2p.rs
add owner_id to SubContract

@@ -218,10 +218,13 @@ impl<'a> P2PNetwork<'a> {
 #[derive(Clone, PartialEq, Eq, Debug)]
 pub struct SubContract {
     /// Identifier for the source entity
-    pub source_id: u8,
+    pub source_id: usize,
+
+    /// Owner of the contract doing the computation
+    pub owner_id: usize,
 
     /// Identifier for the destination entity
-    pub dest_id: u8,
+    pub dest_id: usize,
 
     /// Time remaining (in seconds) before the sub-contract expires
     pub time_left: u32,
@@ -239,9 +242,10 @@ impl SubContract {
     /// # Returns
     ///
     /// A new `SubContract` instance
-    pub fn new(source_id: u8, dest_id: u8, time_left: u32) -> Self {
+    pub fn new(source_id: usize, owner_id: usize, dest_id: usize, time_left: u32) -> Self {
         SubContract {
             source_id,
+            owner_id,
             dest_id,
             time_left,
         }
@@ -266,12 +270,12 @@ impl SubContract {
         }
     }
 
-    /// Checks if the sub-contract has expired
+    /// Checks if the sub-contract has completed
     ///
     /// # Returns
     ///
     /// `true` if expired, `false` otherwise
-    pub fn is_expired(&self) -> bool {
+    pub fn is_complete(&self) -> bool {
         self.time_left == 0
     }
 }

### 2025-04-27 src/backend/p2p.rs
add owner_id to SubContract

@@ -345,7 +345,7 @@ impl<'a> Contract<'a> {
 
         // Check if any sub-contracts are expired
         for layer in &self.layers {
-            if layer.is_expired() {
+            if layer.is_complete() {
                 return false;
             }
         }

### 2025-04-28 src/backend/p2p.rs
change parameters

@@ -152,7 +152,7 @@ impl<'a> P2PNetwork<'a> {
     pub fn optimal_path(
         &self,
         graph: &DirectedGraph<&P2PNode>,
-        order: Vec<&P2PNode>,
+        order: &Vec<&P2PNode>,
         start: usize,
         end: usize,
     ) -> Result<Vec<&P2PNode>, String> {
@@ -588,7 +588,7 @@ impl NodeParameters {
     /// # Returns
     ///
     /// The latency value if it exists, None otherwise
-    pub fn get_latency(&self, destination_node_id: &usize) -> Option<&u32> {
-        self.latencies.get(destination_node_id)
+    pub fn get_latency(&self, destination_node_id: usize) -> Option<&u32> {
+        self.latencies.get(&destination_node_id)
     }
 }

### 2025-04-28 src/main.rs

@@ -11,9 +11,9 @@ fn main() {
     let mut node_params_3 = NodeParameters::new(3, 1, 1);
 
     NodeParameters::set_latency(&mut node_params_0, 1, 5);
-    NodeParameters::set_latency(&mut node_params_1, 1, 9);
-    NodeParameters::set_latency(&mut node_params_2, 1, 2);
-    NodeParameters::set_latency(&mut node_params_3, 1, 7);
+    NodeParameters::set_latency(&mut node_params_1, 2, 9);
+    NodeParameters::set_latency(&mut node_params_2, 3, 2);
+    NodeParameters::set_latency(&mut node_params_3, 0, 7);
 
     let node0 = P2PNode::new(0, node_params_0);
     let node1 = P2PNode::new(1, node_params_1);
@@ -56,9 +56,11 @@ fn main() {
         Err(e) => panic!("Error sorting nodes: {}", e),
     };
 
-    println!("Sorted Nodes");
-    for node in sorted_nodes {
-        let l = NodeParameters::get_latency(&node.params, &1).expect("latency not defined");
-        println!("Node ID: {} Latency to 1: {}", node.id, l);
+    let path =
+        P2PNetwork::optimal_path(&network, &graph, &sorted_nodes, 0, 3).expect("No path found");
+
+    println!("Optimal Path:");
+    for v in path {
+        println!("{}", v.id);
     }
 }

### 2025-04-29 src/backend/p2p.rs
fix ownership and references

@@ -13,16 +13,16 @@ use super::graph::{self, DirectedGraph};
 /// * `end_node_ids` - IDs of nodes that serve as terminal points in the network (at max_layer)
 /// * `min_layer` - The minimum layer range in the network
 /// * `max_layer` - The maximum layer range in the network
-pub struct P2PNetwork<'a> {
-    pub nodes: Vec<P2PNode<'a>>,
+pub struct P2PNetwork {
+    pub nodes: Vec<P2PNode>,
     pub start_node_ids: Vec<usize>,
     pub end_node_ids: Vec<usize>,
     pub min_layer: u8,
     pub max_layer: u8,
-    pub contracts: Vec<Contract<'a>>,
+    pub contracts: Vec<Contract>,
 }
 
-impl<'a> P2PNetwork<'a> {
+impl P2PNetwork {
     /// Creates a new P2PNetwork with empty node vectors and default layer bounds.
     ///
     /// # Returns
@@ -49,7 +49,7 @@ impl<'a> P2PNetwork<'a> {
     /// # Returns
     ///
     /// A new P2PNetwork with nodes categorized appropriately
-    pub fn from_nodes(nodes: Vec<P2PNode<'a>>) -> Self {
+    pub fn from_nodes(nodes: Vec<P2PNode>) -> Self {
         if nodes.is_empty() {
             return Self::new();
         }
@@ -86,7 +86,7 @@ impl<'a> P2PNetwork<'a> {
     /// # Arguments
     ///
     /// * `node` - The node to add to the network
-    pub fn add_node(&mut self, node: P2PNode<'a>) {
+    pub fn add_node(&mut self, node: P2PNode) {
         let node_id = node.id;
         let node_layer = node.params.layer_range;
 
@@ -137,6 +137,29 @@ impl<'a> P2PNetwork<'a> {
         } else if new_layer == self.max_layer {
             self.end_node_ids.push(node_id);
         }
+    }
+
+    /// Gets time in all active sub-contracts for the given node
+    ///
+    /// # Arguments
+    ///
+    /// * `node_id` - Id of node to get time of
+    ///
+    /// # Returns
+    ///
+    /// Time left in the queue for given node
+    pub fn time_in_queue(&self, node_id: usize) -> u32 {
+        let mut total_time = 0;
+
+        for c in self.contracts.iter() {
+            for s in c.layers.iter() {
+                if s.owner_id == node_id {
+                    total_time += s.time_left;
+                }
+            }
+        }
+
[…]

### 2025-04-29 src/main.rs

@@ -9,20 +9,24 @@ fn main() {
     let mut node_params_1 = NodeParameters::new(1, 1, 1);
     let mut node_params_2 = NodeParameters::new(2, 1, 1);
     let mut node_params_3 = NodeParameters::new(3, 1, 1);
+    let mut node_params_4 = NodeParameters::new(1, 10, 1);
 
     NodeParameters::set_latency(&mut node_params_0, 1, 5);
     NodeParameters::set_latency(&mut node_params_1, 2, 9);
-    NodeParameters::set_latency(&mut node_params_2, 3, 2);
+    NodeParameters::set_latency(&mut node_params_2, 4, 2);
     NodeParameters::set_latency(&mut node_params_3, 0, 7);
+    NodeParameters::set_latency(&mut node_params_4, 2, 11);
+    NodeParameters::set_latency(&mut node_params_0, 3, 11);
 
     let node0 = P2PNode::new(0, node_params_0);
     let node1 = P2PNode::new(1, node_params_1);
     let node2 = P2PNode::new(2, node_params_2);
-    let node3 = P2PNode::new(3, node_params_3);
+    let node3 = P2PNode::new(4, node_params_3);
+    let node4 = P2PNode::new(3, node_params_4);
 
-    let nodes = vec![node0, node1, node2, node3];
+    let nodes = vec![node0, node1, node2, node3, node4];
 
-    let network = P2PNetwork::from_nodes(nodes);
+    let mut network = P2PNetwork::from_nodes(nodes);
 
     let graph = P2PNetwork::make_graph(&network);
 
@@ -57,10 +61,10 @@ fn main() {
     };
 
     let path =
-        P2PNetwork::optimal_path(&network, &graph, &sorted_nodes, 0, 3).expect("No path found");
+        P2PNetwork::optimal_path(&network, &graph, &sorted_nodes, 0, 4).expect("No path found");
 
-    println!("Optimal Path:");
-    for v in path {
-        println!("{}", v.id);
-    }
+    let contract =
+        P2PNetwork::create_contract(&network, 0, path).expect("Contract could not be created");
+
+    network.contracts.push(contract);
 }

### 2025-04-29 src/backend/p2p.rs
find shortest path from node

@@ -13,6 +13,7 @@ use super::graph::{self, DirectedGraph};
 /// * `end_node_ids` - IDs of nodes that serve as terminal points in the network (at max_layer)
 /// * `min_layer` - The minimum layer range in the network
 /// * `max_layer` - The maximum layer range in the network
+/// * `contracts` - List of contracts the network has processed
 pub struct P2PNetwork {
     pub nodes: Vec<P2PNode>,
     pub start_node_ids: Vec<usize>,
@@ -162,6 +163,54 @@ impl P2PNetwork {
         total_time
     }
 
+    /// Finds the optimal path for a node to form a complete path in the network
+    /// Search over all start, end combinations and take minimum
+    ///
+    /// # Arguments
+    ///
+    /// * `node` - Node to start from
+    /// * `graph` - DAG representation of P2PNetwork
+    /// * `order` - Sorted list of nodes in graph
+    ///
+    /// # Returns
+    ///
+    /// Gives sequence of node ids that form the shortest path
+    pub fn fastest_path_for_node(
+        &self,
+        node: &P2PNode,
+        graph: &DirectedGraph<&P2PNode>,
+        order: &Vec<&P2PNode>,
+    ) -> Result<Vec<&P2PNode>, String> {
+        let mut min_distance = u32::MAX;
+        let mut shortest_path: Option<Vec<&P2PNode>> = None;
+        for start_node in P2PNetwork::start_nodes(self) {
+            for end_node in P2PNetwork::end_nodes(self) {
+                let start_id = start_node.id;
+                let end_id = end_node.id;
+
+                let distance_to_start = NodeParameters::get_latency(&node.params, start_id)
+                    .expect("latency not defined");
+                let distance_to_end =
+                    NodeParameters::get_latency(&node.params, end_id).expect("latency not defined");
+
+                let (path, distance) =
+                    P2PNetwork::optimal_path(self, graph, order, start_id, end_id)
+                        .expect("path not found");
+
+                let total_distance = distance + distance_to_start + distance_to_end;
+
+                if total_distance < min_distance {
+                    min_distance = total_distance;
+                    shortest_path = Some(path);
+                }
+            }
+        }
+        match shortest_path {
+            Some(path) => Ok(path),
+            None => Err(String::from("No path found in the network")),
+        }
+    }
+
     /// Finds the optimal path between a min and max layer node
[…]

### 2025-04-29 src/main.rs

@@ -59,12 +59,4 @@ fn main() {
         Ok(nodes) => nodes,
         Err(e) => panic!("Error sorting nodes: {}", e),
     };
-
-    let path =
-        P2PNetwork::optimal_path(&network, &graph, &sorted_nodes, 0, 4).expect("No path found");
-
-    let contract =
-        P2PNetwork::create_contract(&network, 0, path).expect("Contract could not be created");
-
-    network.contracts.push(contract);
 }

### 2025-04-29 src/backend/p2p.rs
contracts fix

@@ -189,9 +189,9 @@ impl P2PNetwork {
                 let end_id = end_node.id;
 
                 let distance_to_start = NodeParameters::get_latency(&node.params, start_id)
-                    .expect("latency not defined");
-                let distance_to_end =
-                    NodeParameters::get_latency(&node.params, end_id).expect("latency not defined");
+                    .expect("latency to start not defined");
+                let distance_to_end = NodeParameters::get_latency(&end_node.params, node.id)
+                    .expect("latency from end not defined");
 
                 let (path, distance) =
                     P2PNetwork::optimal_path(self, graph, order, start_id, end_id)
@@ -343,31 +343,39 @@ impl P2PNetwork {
     ///
     /// New contract in network
     pub fn create_contract(&self, owner: usize, nodes: Vec<&P2PNode>) -> Result<Contract, String> {
-        let mut sub_contracts = Vec::new();
+        let mut sub_contracts = VecDeque::new();
 
         let start_node = P2PNetwork::start_nodes(self);
         let end_node = P2PNetwork::end_nodes(self);
 
-        if !start_node.contains(&nodes[1]) {
+        if !start_node.contains(&nodes[nodes.len() - 1]) {
             return Err(String::from("first node is not a start node"));
         }
 
-        if !end_node.contains(&nodes[nodes.len() - 2]) {
+        if !end_node.contains(&nodes[0]) {
             return Err(String::from("last node is not an end node"));
         }
 
-        if nodes[0] != nodes[nodes.len() - 1] {
-            return Err(String::from("first and last nodes do not match"));
-        }
-
-        for i in 1..nodes.len() - 1 {
-            let source_idx = i - 1;
+        for i in 0..nodes.len() {
+            let dest_idx = if i > 0 { i - 1 } else { usize::MAX };
             let owner_idx = i;
-            let dest_idx = i + 1;
+            let source_idx = if i < nodes.len() - 1 {
+                i + 1
+            } else {
+                usize::MAX
+            };
 
-            let source_node = &nodes[source_idx];
+            let source_node = if source_idx == usize::MAX {
+                P2PNetwork::find_node_by_id(self, owner).expect("owner not in network")
+            } else {
+                &nodes[source_idx]
+            };
             let owner_node = &nodes[owner_idx];
-            let dest_node = &nodes[dest_idx];
+            let dest_node = if dest_idx == usize::MAX {
+                P2PNetwork::find_node_by_id(self, owner).expect("owner not in network")
[…]

### 2025-04-29 src/main.rs

@@ -2,7 +2,7 @@ mod backend;
 
 // import p2p network
 use backend::graph::DirectedGraph;
-use backend::p2p::{NodeParameters, P2PNetwork, P2PNode};
+use backend::p2p::{Contract, NodeParameters, P2PNetwork, P2PNode};
 
 fn main() {
     let mut node_params_0 = NodeParameters::new(0, 1, 1);
@@ -12,6 +12,8 @@ fn main() {
     let mut node_params_4 = NodeParameters::new(1, 10, 1);
 
     NodeParameters::set_latency(&mut node_params_0, 1, 5);
+    NodeParameters::set_latency(&mut node_params_0, 0, 0);
+    NodeParameters::set_latency(&mut node_params_4, 0, 3);
     NodeParameters::set_latency(&mut node_params_1, 2, 9);
     NodeParameters::set_latency(&mut node_params_2, 4, 2);
     NodeParameters::set_latency(&mut node_params_3, 0, 7);
@@ -37,11 +39,11 @@ fn main() {
 
     let min_nodes = P2PNetwork::start_nodes(&network);
 
-    for node in min_nodes {
+    for node in min_nodes.iter() {
         println!("Start Node: {}", node.id);
     }
     let max_nodes = P2PNetwork::end_nodes(&network);
-    for node in max_nodes {
+    for node in max_nodes.iter() {
         println!("End Node: {}", node.id);
     }
 
@@ -59,4 +61,20 @@ fn main() {
         Ok(nodes) => nodes,
         Err(e) => panic!("Error sorting nodes: {}", e),
     };
+
+    let first_node = match P2PNetwork::find_node_by_id(&network, 0) {
+        Some(n) => n,
+        None => panic!("Node 0 not found"),
+    };
+
+    let fastest_path =
+        P2PNetwork::fastest_path_for_node(&network, first_node, &graph, &sorted_nodes)
+            .expect("no path found");
+
+    let contract = P2PNetwork::create_contract(&network, 0, fastest_path)
+        .expect("contract could not be created");
+
+    Contract::print(&contract);
+
+    network.contracts.push(contract);
 }

### 2025-04-29 src/backend/p2p.rs
add update network

@@ -40,6 +40,63 @@ impl P2PNetwork {
         }
     }
 
+    /// Update the state of the network after given time period
+    ///
+    /// # Arguments
+    ///
+    /// * `period` - Time in miliseconds
+    pub fn update_network(&mut self, period: u32) -> Vec<usize> {
+        // State of each nodes currently
+        let mut states = vec![false; self.nodes.len()];
+        // If nodes has a pending contract
+        let mut active = vec![false; self.nodes.len()];
+
+        // Process each contract
+        let mut contracts_to_update = Vec::new();
+
+        for contract in self.contracts.iter_mut() {
+            if !contract.fulfilled {
+                active[contract.owner] = true;
+
+                if let Some(sub) = contract.layers.front_mut() {
+                    // owner is in use this round
+                    if !states[sub.owner_id] {
+                        states[sub.owner_id] = true;
+
+                        if !SubContract::tick(sub, period) {
+                            // Store the IDs for later balance update
+                            contracts_to_update.push((sub.price, sub.owner_id, contract.owner));
+                            // Remove the front layer
+                            contract.layers.pop_front();
+                        }
+                    }
+                }
+
+                Contract::fulfill(contract);
+            }
+        }
+
+        // Update balances using the collected information
+        for (price, seller_id, buyer_id) in contracts_to_update {
+            let seller = self
+                .find_node_by_id_mut(seller_id)
+                .expect("owner of contract not found");
+            seller.balance += price;
+
+            let buyer = self
+                .find_node_by_id_mut(buyer_id)
+                .expect("owner of sub contract not found");
+            buyer.balance -= price;
+        }
+
+        // Create contracts for nodes without active contracts
+        active
+            .iter()
+            .enumerate()
+            .filter_map(|(index, &value)| (!value).then_some(index))
+            .collect()
+    }
+
     /// Creates a new P2PNetwork from a list of nodes, automatically determining
     /// which nodes should be considered start nodes and end nodes based on their layer ranges.
     ///
@@ -264,8 +321,9 @@ impl P2PNetwork {
 
                 let queue_time = P2PNetwork::time_in_queue(self, neighbor_id);
                 let processing_time = neighbor.params.computational_cost;
+                let cost = neighbor.price;
 
[…]

### 2025-04-30 src/backend/p2p.rs
optimize network revenue

@@ -3,6 +3,13 @@ use std::hash::{Hash, Hasher};
 
 use super::graph::{self, DirectedGraph};
 
+fn iter_price(old_price: f64, a: u32, c: f64) -> f64 {
+    let ratio = (a * a) as f64 / old_price;
+    let inner = 1.0 - (old_price / a as f64) + (1.0 / c);
+
+    old_price + ratio * inner
+}
+
 /// Represents a peer-to-peer network composed of nodes with specific layer ranges
 /// and connectivity information.
 ///
@@ -95,6 +102,115 @@ impl P2PNetwork {
             .enumerate()
             .filter_map(|(index, &value)| (!value).then_some(index))
             .collect()
+    }
+
+    /// Find share of subcontracts that a node will recieve
+    /// based on the computational costs
+    ///
+    /// # Arguments
+    ///
+    /// * `node` - target node
+    /// * `price` - price that node will charge
+    ///
+    /// # Returns
+    ///
+    /// The percentage of market share the node has
+    pub fn market_share(&self, node: &P2PNode, price: f64) -> f64 {
+        let layer = node.params.layer_range;
+        let cost = node.params.computational_cost;
+
+        let price_per_ms = price / cost as f64;
+
+        let nodes_in_layer: Vec<f64> = self
+            .nodes
+            .iter()
+            .filter_map(|node: &P2PNode| {
+                (node.params.layer_range == layer)
+                    .then_some((-(node.price / node.params.computational_cost as f64)).exp())
+            })
+            .collect();
+
+        let sum: f64 = nodes_in_layer.iter().sum();
+
+        // softmax function
+        (-price_per_ms).exp() as f64 / sum as f64
+    }
+
+    /// Finds the average price per ms in a given layer
+    ///
+    /// # Arguments
+    ///
+    /// * `layer` - Layer to get average on
+    ///
+    /// # Returns
+    ///
+    /// Average price to ms ratio
+    fn layer_avg(&self, layer: u8) -> f64 {
+        let nodes_in_layer: Vec<f64> = self
+            .nodes
+            .iter()
+            .filter_map(|node: &P2PNode| {
+                (node.params.layer_range == layer)
+                    .then_some(node.price / node.params.computational_cost as f64)
+            })
+            .collect();
+
+        let sum: f64 = nodes_in_layer.iter().sum();
+
+        sum / nodes_in_layer.len() as f64
+    }
+
[…]

### 2025-04-30 src/main.rs

@@ -9,7 +9,7 @@ fn main() {
     let mut node_params_1 = NodeParameters::new(1, 1, 1);
     let mut node_params_2 = NodeParameters::new(2, 1, 1);
     let mut node_params_3 = NodeParameters::new(3, 1, 1);
-    let mut node_params_4 = NodeParameters::new(1, 10, 1);
+    let mut node_params_4 = NodeParameters::new(1, 2, 1);
 
     NodeParameters::set_latency(&mut node_params_0, 1, 5);
     NodeParameters::set_latency(&mut node_params_0, 0, 0);
@@ -52,6 +52,10 @@ fn main() {
     for node in nodes_in_graph {
         let neighbors = DirectedGraph::neighbors(&graph, &node);
         println!("Node ID: {} Layer: {}", node.id, node.params.layer_range);
+        println!(
+            "Market Share: {}",
+            P2PNetwork::market_share(&network, node, node.price)
+        );
         for n in neighbors {
             println!("Neighbor {}", n.id);
         }

### 2025-04-30 src/backend/p2p.rs
update main

@@ -764,7 +764,7 @@ impl Contract {
                 println!("    Source ID: {}", subcontract.source_id);
                 println!("    Owner ID: {}", subcontract.owner_id);
                 println!("    Destination ID: {}", subcontract.dest_id);
-                println!("    Time Left: {} seconds", subcontract.time_left);
+                println!("    Time Left: {} ms", subcontract.time_left);
                 println!("    Price: {} tokens", subcontract.price);
             }
         }

### 2025-04-30 src/main.rs

@@ -4,36 +4,37 @@ mod backend;
 use backend::graph::DirectedGraph;
 use backend::p2p::{Contract, NodeParameters, P2PNetwork, P2PNode};
 
+use rand::Rng;
 fn main() {
-    let mut node_params_0 = NodeParameters::new(0, 1, 1);
-    let mut node_params_1 = NodeParameters::new(1, 1, 1);
-    let mut node_params_2 = NodeParameters::new(2, 1, 1);
-    let mut node_params_3 = NodeParameters::new(3, 1, 1);
-    let mut node_params_4 = NodeParameters::new(1, 2, 1);
+    let mut rng = rand::rng();
+    let node_count = vec![2, 3, 1, 3];
+    let mut node_id = 0;
 
-    NodeParameters::set_latency(&mut node_params_0, 1, 5);
-    NodeParameters::set_latency(&mut node_params_0, 0, 0);
-    NodeParameters::set_latency(&mut node_params_4, 0, 3);
-    NodeParameters::set_latency(&mut node_params_1, 2, 9);
-    NodeParameters::set_latency(&mut node_params_2, 4, 2);
-    NodeParameters::set_latency(&mut node_params_3, 0, 7);
-    NodeParameters::set_latency(&mut node_params_4, 2, 11);
-    NodeParameters::set_latency(&mut node_params_0, 3, 11);
+    let mut nodes: Vec<P2PNode> = Vec::new();
 
-    let node0 = P2PNode::new(0, node_params_0);
-    let node1 = P2PNode::new(1, node_params_1);
-    let node2 = P2PNode::new(2, node_params_2);
-    let node3 = P2PNode::new(4, node_params_3);
-    let node4 = P2PNode::new(3, node_params_4);
+    for (layer, num) in node_count.iter().enumerate() {
+        for _ in 0..num.clone() {
+            let new_params = NodeParameters::new(layer as u8, rng.random_range(1..30), 1);
+            let new_node = P2PNode::new(node_id, new_params);
+            nodes.push(new_node);
+            node_id += 1;
+        }
+    }
 
-    let nodes = vec![node0, node1, node2, node3, node4];
+    let total_nodes = nodes.len();
+    for node in nodes.iter_mut() {
+        for dest_id in 0..total_nodes {
+            let params = &mut node.params;
+            NodeParameters::set_latency(params, dest_id, rng.random_range(1..10));
+        }
+    }
 
[…]

### 2025-04-30 src/backend/p2p.rs
fix pricing

@@ -3,13 +3,9 @@ use std::hash::{Hash, Hasher};
 
 use super::graph::{self, DirectedGraph};
 
-fn iter_price(old_price: f64, a: u32, c: f64) -> f64 {
-    let ratio = (a * a) as f64 / old_price;
-    let inner = 1.0 - (old_price / a as f64) + (1.0 / c);
-
-    old_price + ratio * inner
+fn price_gradient(old: f64, prob: f64, cost: u32) -> f64 {
+    prob + (old / cost as f64) * prob * (prob - 1.0)
 }
-
 /// Represents a peer-to-peer network composed of nodes with specific layer ranges
 /// and connectivity information.
 ///
@@ -47,24 +43,42 @@ impl P2PNetwork {
         }
     }
 
+    pub fn nodes_without_contracts(&self) -> Vec<&P2PNode> {
+        // check if there is an active contract for every contract
+        // otherwise return the nodes without active contracts
+        let mut nodes = vec![true; self.nodes.len()];
+
+        for contract in self.contracts.iter() {
+            if contract.fulfilled == false {
+                nodes[contract.owner] = false;
+            }
+        }
+
+        nodes
+            .iter()
+            .enumerate()
+            .filter_map(|(node_id, value)| {
+                value.then_some(
+                    P2PNetwork::find_node_by_id(self, node_id).expect("node not in network"),
+                )
+            })
+            .collect()
+    }
+
     /// Update the state of the network after given time period
     ///
     /// # Arguments
     ///
     /// * `period` - Time in miliseconds
-    pub fn update_network(&mut self, period: u32) -> Vec<usize> {
+    pub fn update_network(&mut self, period: u32) {
         // State of each nodes currently
         let mut states = vec![false; self.nodes.len()];
-        // If nodes has a pending contract
-        let mut active = vec![false; self.nodes.len()];
 
         // Process each contract
         let mut contracts_to_update = Vec::new();
 
         for contract in self.contracts.iter_mut() {
             if !contract.fulfilled {
-                active[contract.owner] = true;
-
                 if let Some(sub) = contract.layers.front_mut() {
                     // owner is in use this round
                     if !states[sub.owner_id] {
@@ -96,12 +110,16 @@ impl P2PNetwork {
             buyer.balance -= price;
         }
 
-        // Create contracts for nodes without active contracts
-        active
-            .iter()
-            .enumerate()
[…]

### 2025-04-30 src/main.rs

@@ -7,14 +7,14 @@ use backend::p2p::{Contract, NodeParameters, P2PNetwork, P2PNode};
 use rand::Rng;
 fn main() {
     let mut rng = rand::rng();
-    let node_count = vec![2, 3, 1, 3];
+    let node_count = vec![2, 4, 2, 4];
     let mut node_id = 0;
 
     let mut nodes: Vec<P2PNode> = Vec::new();
 
     for (layer, num) in node_count.iter().enumerate() {
         for _ in 0..num.clone() {
-            let new_params = NodeParameters::new(layer as u8, rng.random_range(1..30), 1);
+            let new_params = NodeParameters::new(layer as u8, rng.random_range(1..50), 1);
             let new_node = P2PNode::new(node_id, new_params);
             nodes.push(new_node);
             node_id += 1;
@@ -31,61 +31,37 @@ fn main() {
 
     let mut network = P2PNetwork::from_nodes(nodes);
 
-    let graph = P2PNetwork::make_graph(&network);
+    loop {
+        // build graph
+        let graph = P2PNetwork::make_graph(&network);
+        let order = DirectedGraph::topological_sort(&graph)
+            .expect("network has a cycle, graph could not be built");
 
-    println!(
-        "Min Layer: {} Max Layer: {}",
-        network.min_layer, network.max_layer
-    );
-
-    let min_nodes = P2PNetwork::start_nodes(&network);
-
-    for node in min_nodes.iter() {
-        println!("Start Node: {}", node.id);
-    }
-    let max_nodes = P2PNetwork::end_nodes(&network);
-    for node in max_nodes.iter() {
-        println!("End Node: {}", node.id);
-    }
-
-    let nodes_in_graph = DirectedGraph::nodes(&graph);
-
-    for node in nodes_in_graph {
-        let neighbors = DirectedGraph::neighbors(&graph, &node);
-        println!("Node ID: {} Layer: {}", node.id, node.params.layer_range);
-        println!(
-            "Market Share: {}",
-            P2PNetwork::market_share(&network, node, node.price)
-        );
-        for n in neighbors {
-            println!("Neighbor {}", n.id);
+        for node in order.iter() {
+            println!(
+                "ID: {} Rate: {}",
+                node.id,
+                node.price / node.params.computational_cost as f64
+            );
         }
-    }
 
-    let sorted_nodes = match DirectedGraph::topological_sort(&graph) {
-        Ok(nodes) => nodes,
-        Err(e) => panic!("Error sorting nodes: {}", e),
-    };
[…]

### 2025-04-30 src/backend/p2p.rs
fix layer change

@@ -70,7 +70,9 @@ impl P2PNetwork {
     /// # Arguments
     ///
     /// * `period` - Time in miliseconds
-    pub fn update_network(&mut self, period: u32) {
+    /// * `iter` - The current iteration in the simulation
+    /// * `layer_period` - Iteration between finding optimal layer allocation
+    pub fn update_network(&mut self, period: u32, iter: u32, layer_period: u32) {
         // State of each nodes currently
         let mut states = vec![false; self.nodes.len()];
 
@@ -112,13 +114,34 @@ impl P2PNetwork {
 
         // udpate prices that node charge
         let mut new_prices = vec![0.0; self.nodes.len()];
+        let mut new_layers = vec![0u8; self.nodes.len()];
         for node in self.nodes.iter() {
             let new_price = P2PNetwork::update_price(self, node);
             new_prices[node.id] = new_price;
+
+            if iter % layer_period == 0 {
+                new_layers[node.id] = P2PNetwork::find_optimal_layer(self, node);
+            }
         }
 
+        let mut updated_layer = false;
         for node_mut in self.nodes.iter_mut() {
             node_mut.price = new_prices[node_mut.id];
+
+            if !updated_layer && iter % layer_period == 0 {
+                // only update if different
+                if new_layers[node_mut.id] != node_mut.params.layer_range {
+                    P2PNetwork::change_node_layer(
+                        &mut self.start_node_ids,
+                        &mut self.end_node_ids,
+                        self.min_layer,
+                        self.max_layer,
+                        node_mut,
+                        new_layers[node_mut.id],
+                    );
+                    updated_layer = true;
+                }
+            }
         }
     }
 
@@ -193,7 +216,7 @@ impl P2PNetwork {
         let mut max_layer: u8 = node.params.layer_range;
         for layer in self.min_layer..self.max_layer {
             let avg = P2PNetwork::layer_avg(self, layer);
-            if avg > max_avg {
+            if (avg - max_avg) > 0.5 {
                 max_layer = layer;
                 max_avg = avg;
             }
@@ -301,23 +324,30 @@ impl P2PNetwork {
     //
     // * `node` - The node to change in the network
     // * `new_layer` - The new layer range to set
-    pub fn change_node_layer(&mut self, node: &mut P2PNode, new_layer: u8) {
+    fn change_node_layer(
+        start_node_ids: &mut Vec<usize>,
+        end_node_ids: &mut Vec<usize>,
+        min_layer: u8,
+        max_layer: u8,
[…]

### 2025-04-30 src/main.rs

@@ -5,6 +5,8 @@ use backend::graph::DirectedGraph;
 use backend::p2p::{Contract, NodeParameters, P2PNetwork, P2PNode};
 
 use rand::Rng;
+use std::{thread, time};
+
 fn main() {
     let mut rng = rand::rng();
     let node_count = vec![2, 4, 2, 4];
@@ -31,6 +33,7 @@ fn main() {
 
     let mut network = P2PNetwork::from_nodes(nodes);
 
+    let mut iter = 0;
     loop {
         // build graph
         let graph = P2PNetwork::make_graph(&network);
@@ -38,11 +41,7 @@ fn main() {
             .expect("network has a cycle, graph could not be built");
 
         for node in order.iter() {
-            println!(
-                "ID: {} Rate: {}",
-                node.id,
-                node.price / node.params.computational_cost as f64
-            );
+            println!("{}", node.price / node.params.computational_cost as f64);
         }
 
         let nodes_to_process = P2PNetwork::nodes_without_contracts(&network);
@@ -59,9 +58,13 @@ fn main() {
         }
 
         // work on contracts
-        P2PNetwork::update_network(&mut network, 1);
+        P2PNetwork::update_network(&mut network, 1, iter, 500);
 
         // Add all new contracts at once
         network.contracts.extend(new_contracts);
+
+        iter += 1;
+
+        thread::sleep(time::Duration::from_millis(10));
     }
 }

### 2025-04-30 src/backend/p2p.rs
random layer updates

@@ -1,7 +1,6 @@
+use super::graph::{self, DirectedGraph};
 use std::collections::{HashMap, VecDeque};
 use std::hash::{Hash, Hasher};
-
-use super::graph::{self, DirectedGraph};
 
 fn price_gradient(old: f64, prob: f64, cost: u32) -> f64 {
     prob + (old / cost as f64) * prob * (prob - 1.0)
@@ -72,7 +71,13 @@ impl P2PNetwork {
     /// * `period` - Time in miliseconds
     /// * `iter` - The current iteration in the simulation
     /// * `layer_period` - Iteration between finding optimal layer allocation
-    pub fn update_network(&mut self, period: u32, iter: u32, layer_period: u32) {
+    pub fn update_network(
+        &mut self,
+        period: u32,
+        iter: u32,
+        layer_period: u32,
+        node_to_update: usize,
+    ) {
         // State of each nodes currently
         let mut states = vec![false; self.nodes.len()];
 
@@ -124,11 +129,10 @@ impl P2PNetwork {
             }
         }
 
-        let mut updated_layer = false;
         for node_mut in self.nodes.iter_mut() {
             node_mut.price = new_prices[node_mut.id];
 
-            if !updated_layer && iter % layer_period == 0 {
+            if node_mut.id == node_to_update && iter % layer_period == 0 {
                 // only update if different
                 if new_layers[node_mut.id] != node_mut.params.layer_range {
                     P2PNetwork::change_node_layer(
@@ -139,7 +143,6 @@ impl P2PNetwork {
                         node_mut,
                         new_layers[node_mut.id],
                     );
-                    updated_layer = true;
                 }
             }
         }
@@ -211,18 +214,23 @@ impl P2PNetwork {
     ///
     /// Layer range with most expected revenue
     pub fn find_optimal_layer(&self, node: &P2PNode) -> u8 {
+        let node_layer = node.params.layer_range;
         let nodes_avg = node.price / node.params.computational_cost as f64;
         let mut max_avg = nodes_avg;
-        let mut max_layer: u8 = node.params.layer_range;
+        let mut max_layer: u8 = node_layer;
         for layer in self.min_layer..self.max_layer {
             let avg = P2PNetwork::layer_avg(self, layer);
-            if (avg - max_avg) > 0.5 {
+            if avg > max_avg {
                 max_layer = layer;
                 max_avg = avg;
             }
         }
 
-        max_layer
[…]

### 2025-04-30 src/main.rs

@@ -2,13 +2,15 @@ mod backend;
 
 // import p2p network
 use backend::graph::DirectedGraph;
-use backend::p2p::{Contract, NodeParameters, P2PNetwork, P2PNode};
+use backend::p2p::{NodeParameters, P2PNetwork, P2PNode};
 
-use rand::Rng;
+use rand::{Rng, SeedableRng};
+use rand_chacha::ChaCha12Rng;
 use std::{thread, time};
 
 fn main() {
-    let mut rng = rand::rng();
+    //let mut rng = rand::rng();
+    let mut rng = ChaCha12Rng::seed_from_u64(42);
     let node_count = vec![2, 4, 2, 4];
     let mut node_id = 0;
 
@@ -58,7 +60,8 @@ fn main() {
         }
 
         // work on contracts
-        P2PNetwork::update_network(&mut network, 1, iter, 500);
+        let node_to_update = rng.random_range(0..network.nodes.len());
+        P2PNetwork::update_network(&mut network, 1, iter, 1000, node_to_update);
 
         // Add all new contracts at once
         network.contracts.extend(new_contracts);

### 2025-05-01 docs/paper/main.tex
paper template

\documentclass[twoside,11pt]{article}

\usepackage{blindtext}

% Any additional packages needed should be included after jmlr2e.
% Note that jmlr2e.sty includes epsfig, amssymb, natbib and graphicx,
% and defines many common macros, such as 'proof' and 'example'.
%
% It also sets the bibliographystyle to plainnat; for more information on
% natbib citation styles, see the natbib documentation, a copy of which
% is archived at http://www.jmlr.org/format/natbib.pdf

% Available options for package jmlr2e are:
%
%   - abbrvbib : use abbrvnat for the bibliography style
%   - nohyperref : do not load the hyperref package
%   - preprint : remove JMLR specific information from the template,
%         useful for example for posting to preprint servers.
%
% Example of using the package with custom options:
%
% \usepackage[abbrvbib, preprint]{jmlr2e}

\usepackage{jmlr2e}

% Definitions of handy macros can go here

\newcommand{\dataset}{{\cal D}}
\newcommand{\fracpartial}[2]{\frac{\partial #1}{\partial  #2}}

% Heading arguments are {volume}{year}{pages}{date submitted}{date published}{paper id}{author-full-names}

\usepackage{lastpage}
\jmlrheading{23}{2022}{1-\pageref{LastPage}}{1/21; Revised 5/22}{9/22}{21-0000}{Author One and Author Two}

% Short headings should be running head and authors last names

\ShortHeadings{Sample JMLR Paper}{One and Two}
\firstpageno{1}

\begin{document}

\title{Sample JMLR Paper}

\author{\name Author One \email one@stat.washington.edu \\
	\addr Department of Statistics\\
	University of Washington\\
	Seattle, WA 98195-4322, USA
	\AND
	\name Author Two \email two@cs.berkeley.edu \\
	\addr Division of Computer Science\\
	University of California\\
	Berkeley, CA 94720-1776, USA}

\editor{My editor}

\maketitle

\begin{abstract}%   <- trailing '%' for backward compatibility of .sty file
	\blindtext
\end{abstract}

\begin{keywords}
	keyword one, keyword two, keyword three
\end{keywords}

\section{Introduction}

\blindmathpaper

Here is a citation \cite{chow:68}.

% Acknowledgements and Disclosure of Funding should go at the end, before appendices and references

\acks{All acknowledgements go at the end of the paper before appendices and references.
	Moreover, you are required to declare funding (financial activities supporting the
	submitted work) and competing interests (related financial activities outside the submitted work).
	More information about this disclosure can be found on the JMLR website.}

% Manual newpage inserted to improve layout of sample file - not
% needed in general before appendices/bibliography.

\newpage

\appendix
\section{}
\label{app:theorem}

% Note: in this sample, the section number is hard-coded in. Following
% proper LaTeX conventions, it should properly be coded as a reference:

%In this appendix we prove the following theorem from
%Section~\ref{sec:textree-generalization}:

In this appendix we prove the following theorem from
Section~6.2:

\noindent
{\bf Theorem} {\it Let $u,v,w$ be discrete variables such that $v, w$ do
not co-occur with $u$ (i.e., $u\neq0\;\Rightarrow \;v=w=0$ in a given
dataset $\dataset$). Let $N_{v0},N_{w0}$ be the number of data points for
which $v=0, w=0$ respectively, and let $I_{uv},I_{uw}$ be the
respective empirical mutual information values based on the sample
$\dataset$. Then
\[
	N_{v0} \;>\; N_{w0}\;\;\Rightarrow\;\;I_{uv} \;\leq\;I_{uw}
\]
with equality only if $u$ is identically 0.} \hfill\BlackBox

\section{}

\noindent
{\bf Proof}. We use the notation:
\[
	P_v(i) \;=\;\frac{N_v^i}{N},\;\;\;i \neq 0;\;\;\;
	P_{v0}\;\equiv\;P_v(0)\; = \;1 - \sum_{i\neq 0}P_v(i).
\]
These values represent the (empirical) probabilities of $v$
taking value $i\neq 0$ and 0 respectively.  Entropies will be denoted
by $H$. We aim to show that $\fracpartial{I_{uv}}{P_{v0}} < 0$....\\

{\noindent \em Remainder omitted in this sample. See http://www.jmlr.org/papers/ for full paper.}

\vskip 0.2in
\bibliography{main}

\end{document}

### 2025-05-01 src/backend/p2p.rs
fix layer change

@@ -2,8 +2,8 @@ use super::graph::{self, DirectedGraph};
 use std::collections::{HashMap, VecDeque};
 use std::hash::{Hash, Hasher};
 
-fn price_gradient(old: f64, prob: f64, cost: u32) -> f64 {
-    prob + (old / cost as f64) * prob * (prob - 1.0)
+fn price_gradient(old: f64, prob: f64) -> f64 {
+    prob + old * 0.5 * prob * (prob - 1.0)
 }
 /// Represents a peer-to-peer network composed of nodes with specific layer ranges
 /// and connectivity information.
@@ -163,24 +163,26 @@ impl P2PNetwork {
         let layer = node.params.layer_range;
         let cost = node.params.computational_cost;
 
-        let price_per_ms = price / cost as f64;
+        let cost = 0.5 * price + 0.5 * (cost as f64 / 50.0);
 
         let nodes_in_layer: Vec<f64> = self
             .nodes
             .iter()
             .filter_map(|node: &P2PNode| {
-                (node.params.layer_range == layer)
-                    .then_some((-(node.price / node.params.computational_cost as f64)).exp())
+                (node.params.layer_range == layer).then_some(
+                    (-(0.5 * node.price + 0.5 * (node.params.computational_cost as f64 / 50.0)))
+                        .exp(),
+                )
             })
             .collect();
 
         let sum: f64 = nodes_in_layer.iter().sum();
 
         // softmax function
-        (-price_per_ms).exp() as f64 / sum as f64
+        (-cost).exp() as f64 / sum as f64
     }
 
-    /// Finds the average price per ms in a given layer
+    /// Finds the volume of computation in the layer
     ///
     /// # Arguments
     ///
@@ -188,23 +190,21 @@ impl P2PNetwork {
     ///
     /// # Returns
     ///
-    /// Average price to ms ratio
-    fn layer_avg(&self, layer: u8) -> f64 {
+    /// Sum of total computation cost in layer
+    fn layer_volume(&self, layer: u8) -> f64 {
         let nodes_in_layer: Vec<f64> = self
             .nodes
             .iter()
             .filter_map(|node: &P2PNode| {
                 (node.params.layer_range == layer)
-                    .then_some(node.price / node.params.computational_cost as f64)
+                    .then_some((-(node.params.computational_cost as f64 / 50.0)).exp())
             })
             .collect();
 
-        let sum: f64 = nodes_in_layer.iter().sum();
-
[…]

### 2025-05-01 src/main.rs

@@ -43,7 +43,10 @@ fn main() {
             .expect("network has a cycle, graph could not be built");
 
         for node in order.iter() {
-            println!("{}", node.price / node.params.computational_cost as f64);
+            println!(
+                "Layer: {} Node: {} Price: {} Cost: {}",
+                node.params.layer_range, node.id, node.price, node.params.computational_cost
+            );
         }
 
         let nodes_to_process = P2PNetwork::nodes_without_contracts(&network);
@@ -68,6 +71,6 @@ fn main() {
 
         iter += 1;
 
-        thread::sleep(time::Duration::from_millis(10));
+        //thread::sleep(time::Duration::from_millis(10));
     }
 }

### 2025-05-01 docs/paper/main.tex
paper outline

@@
-\documentclass[twoside,11pt]{article}
+\documentclass[preprint,twoside,11pt]{article}
 
@@
 \usepackage{lastpage}
-\jmlrheading{23}{2022}{1-\pageref{LastPage}}{1/21; Revised 5/22}{9/22}{21-0000}{Author One and Author Two}
+\jmlrheading{23}{2022}{1}{1/21}{9/22}{21-0000}{Author One and Author Two}
 
@@
 
-\ShortHeadings{Sample JMLR Paper}{One and Two}
-\firstpageno{1}
-
 \begin{document}
 
-\title{Sample JMLR Paper}
+\title{P2P-LLM: Collaborative LLM Inference}
 
-\author{\name Author One \email one@stat.washington.edu \\
-	\addr Department of Statistics\\
-	University of Washington\\
-	Seattle, WA 98195-4322, USA
-	\AND
-	\name Author Two \email two@cs.berkeley.edu \\
-	\addr Division of Computer Science\\
-	University of California\\
-	Berkeley, CA 94720-1776, USA}
-
-\editor{My editor}
+\author{\name Andrew Boessen \email boessena@bc.edu \\
+}
 
@@
 
-\begin{keywords}
-	keyword one, keyword two, keyword three
-\end{keywords}
-
 \section{Introduction}
 
-\blindmathpaper
+\section{Realted Work}
+
+\subsection{Crowd Computing}
+
+\subsection{P2P Networks}
+
+\section{Peer-to-Peer Network}
+
+\subsection{Path Finding}
+
+\subsection{Revenue Optimization}
+
+\subsection{Network Equilibrium}
+
+\subsection{Strategy-Proofness}
+
+\section{Blockchain}
+
+\subsection{Contracts}
+
+\section{Results}
 
 Here is a citation \cite{chow:68}.
-
-% Acknowledgements and Disclosure of Funding should go at the end, before appendices and references
-
-\acks{All acknowledgements go at the end of the paper before appendices and references.
-	Moreover, you are required to declare funding (financial activities supporting the
-	submitted work) and competing interests (related financial activities outside the submitted work).
-	More information about this disclosure can be found on the JMLR website.}
 
@@
 \section{}
-\label{app:theorem}
-
-% Note: in this sample, the section number is hard-coded in. Following
-% proper LaTeX conventions, it should properly be coded as a reference:
-
-%In this appendix we prove the following theorem from
-%Section~\ref{sec:textree-generalization}:
-
-In this appendix we prove the following theorem from
-Section~6.2:
-
-\noindent
-{\bf Theorem} {\it Let $u,v,w$ be discrete variables such that $v, w$ do
-not co-occur with $u$ (i.e., $u\neq0\;\Rightarrow \;v=w=0$ in a given
-dataset $\dataset$). Let $N_{v0},N_{w0}$ be the number of data points for
-which $v=0, w=0$ respectively, and let $I_{uv},I_{uw}$ be the
-respective empirical mutual information values based on the sample
-$\dataset$. Then
-\[
-	N_{v0} \;>\; N_{w0}\;\;\Rightarrow\;\;I_{uv} \;\leq\;I_{uw}
-\]
-with equality only if $u$ is identically 0.} \hfill\BlackBox
-
-\section{}
-
-\noindent
-{\bf Proof}. We use the notation:
-\[
-	P_v(i) \;=\;\frac{N_v^i}{N},\;\;\;i \neq 0;\;\;\;
-	P_{v0}\;\equiv\;P_v(0)\; = \;1 - \sum_{i\neq 0}P_v(i).
-\]
-These values represent the (empirical) probabilities of $v$
-taking value $i\neq 0$ and 0 respectively.  Entropies will be denoted
-by $H$. We aim to show that $\fracpartial{I_{uv}}{P_{v0}} < 0$....\\
-
-{\noindent \em Remainder omitted in this sample. See http://www.jmlr.org/papers/ for full paper.}
 

### 2025-05-01 src/backend/p2p.rs
first tui

@@ -800,6 +800,14 @@ impl Contract {
         self.fulfilled
     }
 
+    pub fn get_owner(&self) -> usize {
+        self.owner
+    }
+
+    pub fn num_subcontracts(&self) -> usize {
+        self.layers.len()
+    }
+
     /// Prints the contract's state and information about its subcontracts
     ///
     /// This method outputs a formatted representation of the contract,

### 2025-05-01 src/gui/sim.rs

@@ -1,0 +1,464 @@
+use crate::backend::p2p::{Contract, P2PNetwork, P2PNode};
+use crossterm::{
+    event::{self, DisableMouseCapture, EnableMouseCapture, Event, KeyCode},
+    execute,
+    terminal::{disable_raw_mode, enable_raw_mode, EnterAlternateScreen, LeaveAlternateScreen},
+};
+use ratatui::{
+    backend::{Backend, CrosstermBackend},
+    layout::{Constraint, Direction, Layout, Rect},
+    style::{Color, Modifier, Style},
+    text::{Line, Span},
+    widgets::{Block, Borders, Cell, List, ListItem, Paragraph, Row, Table, Tabs},
+    Frame, Terminal,
+};
+use std::{
+    io,
+    sync::{
+        atomic::{AtomicBool, Ordering},
+        Arc, Mutex,
+    },
+    thread,
+    time::{Duration, Instant},
+};
+
+pub enum SimulationSpeed {
+    Paused,
+    Slow,
+    Normal,
+    Fast,
+}
+
+impl SimulationSpeed {
+    fn as_millis(&self) -> Option<u64> {
+        match self {
+            SimulationSpeed::Paused => None,
+            SimulationSpeed::Slow => Some(500),
+            SimulationSpeed::Normal => Some(100),
+            SimulationSpeed::Fast => Some(10),
+        }
+    }
+
+    fn to_string(&self) -> &str {
+        match self {
+            SimulationSpeed::Paused => "Paused",
+            SimulationSpeed::Slow => "Slow",
+            SimulationSpeed::Normal => "Normal",
+            SimulationSpeed::Fast => "Fast",
+        }
+    }
+}
+
+pub struct App {
+    tab_index: usize,
+    network: Arc<Mutex<P2PNetwork>>,
+    simulation_speed: SimulationSpeed,
+    running: Arc<AtomicBool>,
+    selected_node: Option<usize>,
+}
+
+impl App {
+    pub fn new(network: P2PNetwork) -> Self {
+        App {
+            tab_index: 0,
+            network: Arc::new(Mutex::new(network)),
+            simulation_speed: SimulationSpeed::Normal,
+            running: Arc::new(AtomicBool::new(true)),
+            selected_node: None,
+        }
+    }
+
+    pub fn run_simulation(&mut self) -> io::Result<()> {
+        // Setup terminal
+        enable_raw_mode()?;
[…]

### 2025-05-01 src/main.rs

@@ -1,76 +1,54 @@
 mod backend;
+mod gui;
 
 // import p2p network
-use backend::graph::DirectedGraph;
 use backend::p2p::{NodeParameters, P2PNetwork, P2PNode};
+use gui::sim::App;
 
 use rand::{Rng, SeedableRng};
 use rand_chacha::ChaCha12Rng;
-use std::{thread, time};
+use std::{io, process};
 
-fn main() {
-    //let mut rng = rand::rng();
+fn main() -> io::Result<()> {
+    // Set up random number generator with deterministic seed
     let mut rng = ChaCha12Rng::seed_from_u64(42);
+
+    // Define network structure with nodes per layer
     let node_count = vec![2, 4, 2, 4];
     let mut node_id = 0;
-
     let mut nodes: Vec<P2PNode> = Vec::new();
 
+    // Create nodes for each layer
     for (layer, num) in node_count.iter().enumerate() {
-        for _ in 0..num.clone() {
-            let new_params = NodeParameters::new(layer as u8, rng.random_range(1..50), 1);
+        for _ in 0..*num {
+            // Random computational cost between 1-50
+            let comp_cost = rng.gen_range(1..50);
+            let new_params = NodeParameters::new(layer as u8, comp_cost, 1);
             let new_node = P2PNode::new(node_id, new_params);
             nodes.push(new_node);
             node_id += 1;
         }
     }
 
+    // Set up random latencies between nodes
     let total_nodes = nodes.len();
     for node in nodes.iter_mut() {
         for dest_id in 0..total_nodes {
-            let params = &mut node.params;
-            NodeParameters::set_latency(params, dest_id, rng.random_range(1..10));
+            let latency = rng.gen_range(1..10);
+            node.params.set_latency(dest_id, latency);
         }
     }
 
-    let mut network = P2PNetwork::from_nodes(nodes);
+    // Create the P2P network from nodes
+    let network = P2PNetwork::from_nodes(nodes);
 
-    let mut iter = 0;
-    loop {
-        // build graph
-        let graph = P2PNetwork::make_graph(&network);
-        let order = DirectedGraph::topological_sort(&graph)
-            .expect("network has a cycle, graph could not be built");
-
-        for node in order.iter() {
-            println!(
-                "Layer: {} Node: {} Price: {} Cost: {}",
-                node.params.layer_range, node.id, node.price, node.params.computational_cost
-            );
-        }
-
-        let nodes_to_process = P2PNetwork::nodes_without_contracts(&network);
-
[…]

### 2025-05-01 src/gui/sim.rs
update timing

@@ -33,8 +33,8 @@ impl SimulationSpeed {
     fn as_millis(&self) -> Option<u64> {
         match self {
             SimulationSpeed::Paused => None,
-            SimulationSpeed::Slow => Some(500),
-            SimulationSpeed::Normal => Some(100),
+            SimulationSpeed::Slow => Some(100),
+            SimulationSpeed::Normal => Some(50),
             SimulationSpeed::Fast => Some(10),
         }
     }
@@ -81,6 +81,7 @@ impl App {
         let running_clone = Arc::clone(&self.running);
         let simulation_handle = thread::spawn(move || {
             let mut iter = 0;
+            let mut node_to_update = 0;
             while running_clone.load(Ordering::SeqCst) {
                 // Get current speed
                 {
@@ -106,21 +107,24 @@ impl App {
                     }
 
                     // Update network state
-                    let node_to_update = iter as usize % network.nodes.len();
-                    P2PNetwork::update_network(&mut network, 1, iter, 1000, node_to_update);
+                    if iter % 10 == 0 {
+                        node_to_update += 1;
+                        node_to_update = node_to_update % network.nodes.len();
+                    }
+                    P2PNetwork::update_network(&mut network, 1, iter, 10, node_to_update);
 
                     // Add all new contracts at once
                     network.contracts.extend(new_contracts);
                 }
 
                 iter += 1;
-                thread::sleep(Duration::from_millis(100));
+                thread::sleep(Duration::from_millis(200));
             }
         });
 
         // Main rendering loop
         let mut last_tick = Instant::now();
-        let tick_rate = Duration::from_millis(100);
+        let tick_rate = Duration::from_millis(200);
 
         loop {
             terminal.draw(|f| self.ui(f))?;

### 2025-05-01 src/main.rs

@@ -51,4 +51,3 @@ fn main() -> io::Result<()> {
 
     Ok(())
 }
-

### 2025-05-01 src/gui/sim.rs
bar chart

@@ -409,6 +409,12 @@ impl App {
             }
         }
 
+        // Split the area for text stats and bar chart
+        let stats_chunks = Layout::default()
+            .direction(Direction::Vertical)
+            .constraints([Constraint::Percentage(50), Constraint::Percentage(50)].as_ref())
+            .split(area);
+
         // Create a paragraph with statistics
         let stats_text = vec![
             Line::from(vec![
@@ -437,7 +443,7 @@ impl App {
         ];
 
         let mut all_stats = stats_text;
-        for (layer, (avg_price, avg_balance, count)) in layer_stats {
+        for (layer, (avg_price, avg_balance, count)) in &layer_stats {
             all_stats.push(Line::from(vec![
                 Span::raw(format!("Layer {}: ", layer)),
                 Span::styled(
@@ -463,6 +469,74 @@ impl App {
                 .borders(Borders::ALL),
         );
 
-        f.render_widget(stats_widget, area);
+        f.render_widget(stats_widget, stats_chunks[0]);
+
+        // Render bar chart showing node count by layer
+        self.render_layer_bar_chart(f, stats_chunks[1], &layer_stats);
+    }
+
+    fn render_layer_bar_chart<B: Backend>(
+        &self,
+        f: &mut Frame<B>,
+        area: Rect,
+        layer_stats: &[(u8, (f64, f64, usize))],
+    ) {
+        // Find the maximum count for scaling
+        let max_count = layer_stats
+            .iter()
+            .map(|(_, (_, _, count))| *count)
+            .max()
+            .unwrap_or(1);
+
+        // Calculate the width available for each bar
+        let bar_area_width = area.width as usize - 4; // Account for borders and some padding
+        let bar_width = if layer_stats.len() > 0 {
+            bar_area_width / layer_stats.len()
+        } else {
+            1
+        };
+
+        // Create a block for the bar chart
+        let block = Block::default()
+            .title("Nodes Per Layer")
+            .borders(Borders::ALL);
+        let inner_area = block.inner(area);
+
+        f.render_widget(block, area);
+
+        // Render each bar
+        for (i, (layer, (_, _, count))) in layer_stats.iter().enumerate() {
+            let bar_height = ((count * (inner_area.height as usize - 1)) / max_count) as u16;
+            let bar_height = bar_height.max(1); // Ensure at least 1 height
+
+            let bar_x = inner_area.left() + (i * bar_width) as u16;
+            let bar_y = inner_area.bottom() - bar_height;
+
[…]

### 2025-05-01 src/backend/p2p.rs
optimal path

@@ -420,11 +420,20 @@ impl P2PNetwork {
                     .expect("latency from end not defined")
                     .clone();
 
+                let start_cost = P2PNetwork::time_in_queue(self, start_id)
+                    + start_node.params.computational_cost;
+                let end_cost =
+                    P2PNetwork::time_in_queue(self, end_id) + end_node.params.computational_cost;
+
                 let (path, distance) =
                     P2PNetwork::optimal_path(self, graph, order, start_id, end_id)
                         .expect("path not found");
 
-                let total_distance = distance + distance_to_start as f64 + distance_to_end as f64;
+                let total_distance = distance
+                    + distance_to_start as f64
+                    + distance_to_end as f64
+                    + start_cost as f64
+                    + end_cost as f64;
 
                 if total_distance < min_distance {
                     min_distance = total_distance;

### 2025-05-01 src/main.rs

@@ -14,7 +14,7 @@ fn main() -> io::Result<()> {
     let mut rng = ChaCha12Rng::seed_from_u64(42);
 
     // Define network structure with nodes per layer
-    let node_count = vec![2, 4, 2, 4];
+    let node_count = vec![10, 4, 10, 4];
     let mut node_id = 0;
     let mut nodes: Vec<P2PNode> = Vec::new();
 

### 2025-05-02 src/gui/sim.rs
change sleep duration

@@ -118,13 +118,13 @@ impl App {
                 }
 
                 iter += 1;
-                thread::sleep(Duration::from_millis(200));
+                thread::sleep(Duration::from_millis(100));
             }
         });
 
         // Main rendering loop
         let mut last_tick = Instant::now();
-        let tick_rate = Duration::from_millis(200);
+        let tick_rate = Duration::from_millis(100);
 
         loop {
             terminal.draw(|f| self.ui(f))?;

### 2025-05-03 docs/paper/main.tex
related work section

@@
 \usepackage{jmlr2e}
+\usepackage{tikz}
+\usetikzlibrary{positioning}
+\usepackage{amssymb}
+\usepackage{amsmath}
+\usepackage{tcolorbox}
+\usepackage{mathtools}
+\usepackage{enumerate}
+\usepackage{algorithm}
+\usepackage{algorithmicx}
+\usepackage{algpseudocode}
 
@@
 
+In recent years, large language models (LLMs) have demonstrated remarkable capabilities across diverse tasks,
+exhibiting unprecedented rates of improvement within a relatively brief developmental timeline.
+This extraordinary progress can be primarily attributed to the immense computational resources allocated to training these models on datasets comprising
+trillions of tokens, resulting in systems that subsequently demand substantial computing power for deployment.
+The computational intensity of these models has resulted in significant investment,
+with billions of dollars directed toward the construction of specialized super-clusters housing hundreds of thousands of GPUs dedicated to the training and serving of LLMs.
+Given the substantial memory and computational requirements of state-of-the-art LLMs, most personal computing devices lack the necessary specifications to run or train these models independently.
+Consequently, access to LLM capabilities is predominantly channeled through services offered by large technology corporations, which may present concerns regarding privacy, autonomy, and accessibility.
+
+Crowdsourcing methodologies offer a promising alternative to address these limitations.
+The crowdsourcing approach has demonstrated considerable success across various domains, including knowledge aggregation (Wikipedia),
+real-time traffic information collection (Waze), and venture capital formation (Kickstarter).
+These same foundational principles can be effectively applied to computational resource allocation and utilization.
+
+My work explores fully decentralized crowd computing architectures,
+where users establish a peer-to-peer network in which each participant can leverage the collective computational resources for individual tasks.
+This structure shares conceptual similarities with BitTorrent file-sharing networks.
+While current state-of-the-art language models exceed the capacity of individual personal computers,
+the aggregation of distributed computational resources through a decentralized network could potentially enable users to host their own LLMs,
+thereby democratizing access to advanced artificial intelligence capabilities.
 \section{Realted Work}
@@
 
+The idea of pooling compute power from many computers to form a distributed supercomputer is not new. This concept of Crowd Computing
+has been used ever since large networks of computer were formed. The predominant use of this method is to fascilitate academic research.
+Researchers publish problem that that are working on, and anyone can help contribute by volunteering to donate computing power.
+Projects that have successfully used crowd computing include SETI@Home \citep{10.1145/581571.581573} and Einstein@Home \citep{Steltner_2021}.
+This approach has proven to be successful in the past, but it has become less popular as the computational power of computers increased and access to supercomputers increased.
+However, the use of idle compute power still has untapped applications, and the principles from crowd computing can be applied to modern tasks like LLM inference.
+
 \subsection{P2P Networks}
 
+LLM inference is a perfect candidate for P2P network because it has technical requirments that prohibit most personal computers from being able to run
+large models with billions of parameters, and it can easilly be split into small chunks that can be run on several computers at the same time. The most notable research
+being done in this area is Petals \citep{borzunov2023petalscollaborativeinferencefinetuning} which is a BitTorrent like peer-to-peer network for LLM inference and finetuning.
+Petals creates a network with client and servers.
+Clients send requests that will be processed by the servers on the network.
+The model is split into multiple sequential blocks of layers, and each server
+in the network is capable of serving one or multiple of these blocks. In order to run an inference step, a client will find a optimal path of servers
+in the network thats forms the complete model and minimizes time required. In my work I explore a similar approach with a network of distributed computers that serve a specific part of the whole LLM,
+but I expand upon this and add incentive mechanisms that reward nodes for donating their computational power.
+This incentive mechanism also fucilitates optimal allocation of nodes to maximize throughput, by each
+node maximizing expected revenue individually.
+
 \section{Peer-to-Peer Network}
+
+Fundamentally, a peer-to-peer network is a decentralized system where each devices acts as a client and a sever.
+Each devices can send and recieve data which eliminates the need for a centralized server. The central benefit of a P2P network
+is that recources are pooled and shared between peers, so the combined resources available to an individual peer is greater than that nodes own resources.
+A peer-to-peer network can be built to share any type of resource. In the case of BitTorrent, bandwidth and files are shared between peers.
+For the case of LLM inference, peers will need to ba able to share bandwidth, data, and computational power.
+
+\begin{figure}
+	\centering
+	\begin{tikzpicture}[
+			node distance=2cm and 3cm,
+			every node/.style={draw, circle, minimum size=1.25cm},
+			>=stealth,
+		]
+		% Layer 1 nodes
+		\node[] (A1) at (0,2) {$0$};
+		\node[] (A2) at (0,0) {$1$};
+		\node[] (A3) at (0,-2) {$2$};
+
+		% Layer 2 nodes
+		\node[] (B1) at (3,1) {$3$};
+		\node[] (B2) at (3,-1) {$4$};
+
+		% Layer 3 node
+		\node[] (C1) at (6,0) {$5$};
+
+		% Layer 4 nodes
+		\node[] (D1) at (9,2) {$6$};
+		\node[] (D2) at (9,0) {$7$};
+		\node[] (D3) at (9,-2) {$8$};
+
+		% Connections from Layer 1 to Layer 2
+		\draw[->] (A1) -- (B1);
+		\draw[->] (A1) -- (B2);
+		\draw[->] (A2) -- (B1);
+		\draw[->] (A2) -- (B2);
+		\draw[->] (A3) -- (B1);
+		\draw[->] (A3) -- (B2);
+
+		% Connections from Layer 2 to Layer 3
+		\draw[->] (B1) -- (C1);
+		\draw[->] (B2) -- (C1);
+
+		% Connections from Layer 3 to Layer 4
+		\draw[->] (C1) -- (D1);
+		\draw[->] (C1) -- (D2);
+		\draw[->] (C1) -- (D3);
+
+		% Labels for the layers
+		\node[draw=none, above=0cm of A1] {Layer 1};
+		\node[draw=none, above=1cm of B1] {Layer 2};
+		\node[draw=none, above=2cm of C1] {Layer 3};
+		\node[draw=none, above=0cm of D1] {Layer 4};
+	\end{tikzpicture}
+	\caption{P2P-LLM Network Directed Graph}
+	\label{fig:layered_graph}
+\end{figure}
 
@@
 
-\section{Blockchain}
+\section{Cryptoeconomics}
+
+\subsection{Blockchain}
 
@@
 
+\section{Experiment Setup}
+
 \section{Results}
-
-Here is a citation \cite{chow:68}.
 
@@
 \appendix
-\section{}
+\section{Topological Sort}
+\begin{algorithm}
+	\caption{Topological Sort of a Directed Acyclic Graph (DAG)}
+	\begin{algorithmic}[1]
+		\Require{A directed acyclic graph $G = (V, E)$}
+		\Ensure{A linear ordering of vertices such that for every directed edge $(u, v)$, vertex $u$ comes before vertex $v$}
+
+		\State $\text{result}[]$ \Comment An empty list to store the sorted vertices
+		\State $\text{visited}[v] \rightarrow $false for all $v \in V$ \Comment A map to track visited vertices
+		\State $\text{temp}[v] \rightarrow $ false for all$ v \in V$ \Comment A map to track vertices in the current recursion stack
+
+		\For{each vertex $v \in V$}
+		\If{$\text{visited}[v] = \text{false}$}
+		\State DFS-Visit($G$, $v$, $\text{visited}$, $\text{temp}$, $\text{result}$)
+		\EndIf
+		\EndFor
+
+		\State \Return Reverse($\text{result}$)
+
+		\Function{DFS-Visit}{$G$, $u$, $\text{visited}$, $\text{temp}$, $\text{result}$}
+		\State $\text{temp}[u] \gets \text{true}$ \Comment{Mark current vertex as being processed}
+
+		\For{each vertex $v$ such that $(u, v) \in E$}
+		\State DFS-Visit($G$, $v$, $\text{visited}$, $\text{temp}$, $\text{result}$)
+		\EndFor
+
+		\State $\text{temp}[u] \gets \text{false}$ \Comment{Mark $u$ as processed}
+		\State $\text{visited}[u] \gets \text{true}$ \Comment{Mark $u$ as visited}
+		\State Append $u$ to $\text{result}$
+		\EndFunction
+	\end{algorithmic}
+\end{algorithm}
+
+\section{Shortest Path}
+\begin{algorithm}
+	\caption{Shortest Path in a DAG}
+	\begin{algorithmic}[1]
+		\Require{Graph $G = (V, E)$ with edge weights $w$, source vertex $s$, target vertex $t$, topological ordering $topo[]$ of $G$}
+		\Ensure{Length of shortest path from $s$ to $t$ and the path itself}
+
+		\State Initialize $dist[v] \gets \infty$ for all $v \in V$
+		\State Initialize $prev[v] \gets \text{nil}$ for all $v \in V$
+		\State $dist[s] \gets 0$
+
+		\For{each vertex $u$ in topological order $topo[]$}
+		\For{each outgoing edge $(u, v) \in E$}
+		\If{$dist[v] > dist[u] + w(u, v)$}
+		\State $dist[v] \gets dist[u] + w(u, v)$
+		\State $prev[v] \gets u$
+		\EndIf
+		\EndFor
+		\EndFor
+
+		\State $path \gets \emptyset$ \Comment{Reconstruct the shortest path}
+		\State $curr \gets t$
+		\While{$curr \neq \text{nil}$}
+		\State Prepend $curr$ to $path$
+		\State $curr \gets prev[curr]$
+		\EndWhile
+
+		\State \Return $dist[t]$, $path$
+	\end{algorithmic}
+\end{algorithm}
 

### 2025-05-03 docs/paper/main.tex
path finding section

@@
 \usepackage{algpseudocode}
+\usepackage{pgfplots}
+\pgfplotsset{compat=1.18}
 
@@
 LLM inference is a perfect candidate for P2P network because it has technical requirments that prohibit most personal computers from being able to run
-large models with billions of parameters, and it can easilly be split into small chunks that can be run on several computers at the same time. The most notable research
-being done in this area is Petals \citep{borzunov2023petalscollaborativeinferencefinetuning} which is a BitTorrent like peer-to-peer network for LLM inference and finetuning.
+large models with billions of parameters, and it can easilly be split into small chunks that can be run on several computers at the same time.
+BitWorker \citep{Durand_Gasparyan_Rouvinez_Aad_Braun_Trinh_2015} is a protocol designed to compute any parallel computing task across a peer-to-peer network.
+Although it is possible to apply LLM inference to this protocol, BitWorker is designed for general tasks and would not able to efficiently scale to the demands of many users.
+The most notable research being done in this area is Petals \citep{borzunov2023petalscollaborativeinferencefinetuning} which is a BitTorrent like peer-to-peer network for LLM inference and finetuning.
 Petals creates a network with client and servers.
@@
 For the case of LLM inference, peers will need to ba able to share bandwidth, data, and computational power.
+
+A peer-to-peer network is defined as having $n$ nodes in the network. There is an LLM model with $m$ total layers which will be devided between nodes.
+Each node $N$ in the network is a tuple $N(\ell, l, c, p)$ where $\ell _i = (x,y) : x,y \in [0,m); y > x$ is the range of layers the node is able to serve, $l_{ij}$ is the network latency between nodes $i$ and $j$,
+$c_i$ is the computational cost of the node, measured in miliseconds, and $p_i$ is the price the nodes charges for its compute.
+
+\subsection{Path Finding}
+
+In order to use the network to run the LLM, a node must first find a sequence of nodes in the graph that form a complete model.
+Because the LLM layers must be computed sequentially, the node must find a path through the network that ideally will compute
+the LLM in the least amount of time possible and at the lowest price. This problem can be solved by viewing the network as a directed graph where weight correspond
+to the computational cost of nodes. The edges of the graph correspond the compatability between the layers that each node in serving.
+Specifically, every node is connected to all nodes that are serving the consecutive layer of the model. A vizualization of this directed graph is shown in Figure \ref{fig:layered_graph}.
 
@@
 
-\subsection{Path Finding}
+Due to this property, the P2P network graph is a directed acyclical graph (DAG). This means that there are efficient
+algorithms to find the shortest path between two nodes. The first step is to perform a topological sort on the nodes in the network.
+This is an ordering of the nodes such that all neighbors of a node come after the node in the ordering.
+For example, a topological ordering of the DAG in Figure \ref{fig:layered_graph} is $[0,1,2,3,4,5,6,7,8]$.
+The algorithm for topological sort is shown in Appendix \ref{app:topo_sort}. With the topological order, dynamic programming can be used to find the shortest path in the network.
+This algorithm will iterate over the ordering, and search all the nodes neighbors for the one with the lowest weight.
+The full algorithm is shown in Appendix \ref{app:shortest_path}. Most importantly, both the topological sort and path finding algorithm run in linear time
+with a computational complexity of $O(|V| + |E|)$.
+
+\subsection{Pareto Effeciency}
+
+The optimal path is well defined when weights for nodes are clearly defined, but there is not a clear way to define
+weights for nodes in this case. In the P2P-LLM network there are two competing criterea that define the weight of node: computational cost and price.
+The algorithm described above uses a single objective, while the optimal path in the network is a multi-objective optimization problem.
+
+\begin{tikzpicture}
+	\begin{axis}[
+			width=12cm,
+			height=10cm,
+			xlabel={Computational Cost},
+			ylabel={Price},
+			xlabel style={font=\large},
+			ylabel style={font=\large},
+			xmin=0, xmax=10,
+			ymin=0, ymax=10,
+			xtick={0,2,4,6,8,10},
+			ytick={0,2,4,6,8,10},
+			grid=both,
+			title={Pareto Frontier: Computational Cost vs. Price},
+			legend pos=north east,
+			legend style={font=\footnotesize}
+		]
+
+		% Scatter plot of solutions
+		\addplot[only marks, mark=o, mark size=3pt, blue] coordinates {
+				(2,9) (3,7.2) (4,6) (5,5) (6,4.3) (7,3.8) (8,3.5) (9,3.2)
+			};
+
+		% Pareto frontier
+		\addplot[thick, red, smooth] coordinates {
+				(2,9) (3,7.2) (4,6) (5,5) (6,4.3) (7,3.8) (8,3.5) (9,3.2)
+			};
+
+		% Sample dominated solutions
+		\addplot[only marks, mark=x, mark size=3pt, gray] coordinates {
+				(2.5,9.5) (3.5,8) (4.5,7) (5.5,6) (6.5,5.8) (7.5,5) (8.5,4.5)
+				(3,8.5) (4,7.5) (5,6.5) (6,5.5) (7,4.7) (8,4.2)
+			};
+
+		% Ideal point (non-achievable)
+		\addplot[only marks, mark=star, mark size=5pt, green!70!black] coordinates {
+				(2,2)
+			};
+
+		% Add legend
+		\legend{Pareto-optimal Solutions, Pareto Frontier, Dominated Solutions, Ideal Point};
+
+	\end{axis}
+\end{tikzpicture}
 
@@
 \section{Topological Sort}
+\label{app:topo_sort}
 \begin{algorithm}
@@
 \section{Shortest Path}
+\label{app:shortest_path}
 \begin{algorithm}

### 2025-05-03 docs/paper/main.tex
MO optimization

@@
 A peer-to-peer network is defined as having $n$ nodes in the network. There is an LLM model with $m$ total layers which will be devided between nodes.
-Each node $N$ in the network is a tuple $N(\ell, l, c, p)$ where $\ell _i = (x,y) : x,y \in [0,m); y > x$ is the range of layers the node is able to serve, $l_{ij}$ is the network latency between nodes $i$ and $j$,
-$c_i$ is the computational cost of the node, measured in miliseconds, and $p_i$ is the price the nodes charges for its compute.
+Each node $N$ in the network is a tuple $N(\ell, l, c, p)$ where
+\begin{enumerate}
+  \item $\ell _i = (x,y) : x,y \in [0,m); y > x$ is the range of layers the node is able to serve
+  \item $l_{ij} \in \mathbb{R}$ is the network latency between nodes $i$ and $j$,
+  \item $c_i \in \mathbb{R}$ is the computational cost of the node, measured in miliseconds
+  \item $p_i \in \mathbb{R}$ is the price the nodes charges for its compute.
+\end{enumerate}
 
@@
 weights for nodes in this case. In the P2P-LLM network there are two competing criterea that define the weight of node: computational cost and price.
-The algorithm described above uses a single objective, while the optimal path in the network is a multi-objective optimization problem.
+The algorithm described above uses a single objective (SO), while the optimal path in the network is a multi-objective (MO) optimization problem.
+There are several way to find optimal solutions to MO optimization problems \citep{1599245}. The simplest way is to convert it to a SO optimization problem, and
+since the shortest path algorithm is designed for SO objective, it is the most practical solution for this task. In order to reframe the problem as a single objective,
+a weighed aggreagte of the objetives is used. In the case for the peer-to-peer network, the SO is a weighed sum of computational cost $c_i$ and price $p_i$.
+The objective, or weight of a node, $w_i$ is defined as.
+$$w_i = \alpha c_i + 1 - \alpha p_i$$
 

### 2025-05-03 docs/paper/main.tex
Pareto

@@
 Each node $N$ in the network is a tuple $N(\ell, l, c, p)$ where
-\begin{enumerate}
+\begin{itemize}
 	\item $\ell _i = (x,y) : x,y \in [0,m); y > x$ is the range of layers the node is able to serve
@@
 	\item $p_i \in \mathbb{R}$ is the price the nodes charges for its compute.
-\end{enumerate}
+\end{itemize}
 
@@
 In order to use the network to run the LLM, a node must first find a sequence of nodes in the graph that form a complete model.
-Because the LLM layers must be computed sequentially, the node must find a path through the network that ideally will compute
-the LLM in the least amount of time possible and at the lowest price. This problem can be solved by viewing the network as a directed graph where weight correspond
+Because the LLM layers must be computed sequentially, the node must find a path through the network that will ideally compute
+the LLM in the least amount of time possible and at the lowest price. This problem can be solved by viewing the network as a directed graph where weights correspond
 to the computational cost of nodes. The edges of the graph correspond the compatability between the layers that each node in serving.
@@
 This is an ordering of the nodes such that all neighbors of a node come after the node in the ordering.
+For any graph $G = (V, E)$ a totological ordering is an order $\prec$ on $V$ such that if $(u \rightarrow v) \in E$ then $u \prec v$.
 For example, a topological ordering of the DAG in Figure \ref{fig:layered_graph} is $[0,1,2,3,4,5,6,7,8]$.
 The algorithm for topological sort is shown in Appendix \ref{app:topo_sort}. With the topological order, dynamic programming can be used to find the shortest path in the network.
-This algorithm will iterate over the ordering, and search all the nodes neighbors for the one with the lowest weight.
+This algorithm will iterate over the ordering, and search all the node's neighbors for the one with the lowest weight.
 The full algorithm is shown in Appendix \ref{app:shortest_path}. Most importantly, both the topological sort and path finding algorithm run in linear time
@@
 a weighed aggreagte of the objetives is used. In the case for the peer-to-peer network, the SO is a weighed sum of computational cost $c_i$ and price $p_i$.
-The objective, or weight of a node, $w_i$ is defined as.
-$$w_i = \alpha c_i + 1 - \alpha p_i$$
+The objective, or weight, of a node, $w_i$ is defined as.
+$$w_i = \alpha \cdot c_i + (1 - \alpha) \cdot p_i$$
+Howver, this assumes that the weight $\alpha$ is known a priori. In general, there are many equivilent optimal solutions in a MO optimzation problem.
+These are known and Pareto-optimal solutions. They are solutions such that there is no way to improve one objective without degrading any other objectives.
+A solution is said to be Pareto-optimal if there are no other solutions that dominate it. A solution $x_1$ dominates $x_2$ if
+\begin{enumerate}
+	\item $\forall i, f_i(x_1) \leq f_i(x_2)$
+	\item $\exists i, f_i(x_1) < f_i(x_2)$
+\end{enumerate}
+where $f_i()$ is the utility for the $i$th objective.
+The set of all Pareto-optimal solutions forms a frontier (Figure \ref{fig:Pareto-optimal}) of equivilent solutions, but there is not a clear choice on which one should be used.
+In the case of the SO weighted aggreagte used in the P2P-LLM network, the parameter $\alpha$ decides where on the Pareto frontier the optimal solution lies.
+Due to this, each node can independently decide that importance of price and computational cost in the optimal path through the network.
 
+\begin{figure}
+	\centering
 	\begin{tikzpicture}
@@
 				width=12cm,
-			height=10cm,
+				height=8cm,
 				xlabel={Computational Cost},
@@
 	\end{tikzpicture}
+	\caption{Pareto Frontier}
+	\label{fig:Pareto-optimal}
+\end{figure}
 
@@
 
+\begin{figure}
+	\centering
+	\begin{tikzpicture}
+		\begin{axis}[
+				width=14cm,
+				height=8cm,
+				xlabel={$p_i$},
+				ylabel={Expected Revenue $R(p_i, c_i)$},
+				domain=0:12,
+				samples=200,
+				legend pos=north east,
+				grid=major,
+				thick,
+				every axis plot/.append style={very thick},
+				title={Expected Revenue Function $R(p_i, c_i)$}
+			]
+
+			% Constant denominator
+			\def\C{0.05}
+
+			% Plot the function for different constants in numerator
+			\addplot[color=blue] {(x)*(exp(-(0.5*x+0.5))/(exp(-(0.5*x+0.5)) +\C))};
+			\addlegendentry{$c_i = 1$}
+			\addplot[color=green] {(x)*(exp(-(0.5*x+1))/(exp(-(0.5*x+1)) +\C))};
+			\addlegendentry{$c_i = 2$}
+			\addplot[color=red] {(x)*(exp(-(0.5*x+2))/(exp(-(0.5*x+2)) +\C))};
+			\addlegendentry{$c_i = 4$}
+
+		\end{axis}
+	\end{tikzpicture}
+	\caption{Expected Revenue}
+	\label{fig:exp_rev}
+\end{figure}
 \subsection{Network Equilibrium}

### 2025-05-04 docs/paper/main.tex
optimal pricing

@@
 \pgfplotsset{compat=1.18}
+\usepackage[thinc]{esdiff}
 
@@
 \begin{abstract}%   <- trailing '%' for backward compatibility of .sty file
-	\blindtext
 \end{abstract}
@@
 The objective, or weight, of a node, $w_i$ is defined as.
-$$w_i = \alpha \cdot c_i + (1 - \alpha) \cdot p_i$$
-Howver, this assumes that the weight $\alpha$ is known a priori. In general, there are many equivilent optimal solutions in a MO optimzation problem.
-These are known and Pareto-optimal solutions. They are solutions such that there is no way to improve one objective without degrading any other objectives.
-A solution is said to be Pareto-optimal if there are no other solutions that dominate it. A solution $x_1$ dominates $x_2$ if
-\begin{enumerate}
-	\item $\forall i, f_i(x_1) \leq f_i(x_2)$
-	\item $\exists i, f_i(x_1) < f_i(x_2)$
-\end{enumerate}
-where $f_i()$ is the utility for the $i$th objective.
-The set of all Pareto-optimal solutions forms a frontier (Figure \ref{fig:Pareto-optimal}) of equivilent solutions, but there is not a clear choice on which one should be used.
-In the case of the SO weighted aggreagte used in the P2P-LLM network, the parameter $\alpha$ decides where on the Pareto frontier the optimal solution lies.
-Due to this, each node can independently decide that importance of price and computational cost in the optimal path through the network.
+
+\begin{equation}
+	w_i = \alpha \cdot p_i + (1 - \alpha) \cdot c_i
+	\label{eq:weight}
+\end{equation}
 
@@
 
+However, this assumes that the weight $\alpha$ is known a priori. In general, there are many equivilent optimal solutions in a MO optimzation problem.
+These are known and Pareto-optimal solutions. They are solutions such that there is no way to improve one objective without degrading any other objectives.
+A solution is said to be Pareto-optimal if there are no other solutions that dominate it. A solution $x_1$ dominates $x_2$ if
+\begin{enumerate}
+	\item $\forall i, f_i(x_1) \leq f_i(x_2)$ and
+	\item $\exists i, f_i(x_1) < f_i(x_2)$
+\end{enumerate}
+where $f_i()$ is the utility for the $i$th objective.
+
+The set of all Pareto-optimal solutions forms a frontier (Figure \ref{fig:Pareto-optimal}) of equivilent solutions, but there is not a clear choice on which one should be used.
+In the case of the SO weighted aggreagte used in the P2P-LLM network, the parameter $\alpha$ decides where on the Pareto frontier the optimal solution lies.
+Due to this, each node can independently decide that importance of price and computational cost in the optimal path through the network.
+
 \subsection{Revenue Optimization}
+
+Each peer additionally has to choose a price to charge for other peers to use their computation.
+Ideally each node will act in its self-iterest and choose the price that maximizes revenue.
+If the price is too high, peers will choose equivlent node serving the same layers,
+while if the price is too low, the total revenue will be less than ideal.
+The price they choose should reflect the current state of the network, and adapt to conditions.
+In this context, price optimization become difficult as it is a dynamic environment
+and a uniform pricing rule would not result in optimal revenue.
+In the P2P-LLM network, a peer only has to compete with other peers serving the same layers.
+This can be exploited to narrow down the complexities of this problem.
+Working with this leads to the conclusion that a nodes price should be determined
+by its own price and computational cost and the price and computational cost of all other peers serving the same layers.
 
@@
 				xlabel={$p_i$},
-				ylabel={Expected Revenue $R(p_i, c_i)$},
+				ylabel={Expected Revenue $R(p_i)$},
 				domain=0:12,
@@
 				every axis plot/.append style={very thick},
-				title={Expected Revenue Function $R(p_i, c_i)$}
+				title={Expected Revenue Function $R(p_i)$}
 			]
@@
 	\end{tikzpicture}
-	\caption{Expected Revenue}
+	\caption{Effect of Computational Cost on Expected Revenue}
 	\label{fig:exp_rev}
 \end{figure}
+
+If we can define a revenue function based on these parameters, then the optimal price can be found by maximizing this function with respect to $p_i$.
+The revenue a node recieves for a single peer using the network would be its price multiplied by the probability of being chosen in the optimal path.
+
+\begin{equation}
+	R(p_i) = p_i \cdot \mathbb{P}(w_i)
+	\label{eq:revenue}
+\end{equation}
+
+The probability that a node is chosen is related to its weight (Equation \ref{eq:weight}).
+In order to get a distribution across all weights in the node's layer, the Boltzmann distribution \citep{boltzmann1868studien} can be used.
+This distribution give the probability that a system will be in certain state.
+
+\begin{equation}
+	\mathbb{P}(\epsilon_i) = \frac{e^{- \epsilon_i / kT}}{\sum_{j=1}^{M}e^{- \epsilon_j / kT}}
+	\label{eq:Boltzmann}
+\end{equation}
+
+where $\epsilon_i$ is the energy for state $i$, $k$ is the Boltzmann constant, and $T$ is the temperature of the system.
+For the purposes of the P2P-LLM network, $k$ and $T$ are dropped and $\epsilon_i$ is $w_i$ (Equation \ref{eq:weight}).
+Using this method gives a smooth expected revenue function, and prices will reflect how much each nodes contributes to the network.
+Specifcally, if a nodes contributes more compute power to the network, demonstrated as a lower computational cost $c_i$, the optimal
+price they will charge will be higher, and they will be rewarded with a higher expected revenue.
+A vizualization of how $c_i$ effects the expected revenue curve is shown in Figure \ref{fig:exp_rev}.
+
+Now with the expected revnue function, the optimal price can be found by finding the price that maximizes $R(p_i)$.
+Unfortunately, there is not a closed form solution to this problem, but there are methods that can be used.
+Iterative pricing mechanism \citep{ecf80b8b-07bb-374f-ab3f-2cc6a349f689} are used to find optimal prices by making iterative changes to the price until it converages at an optimal point.
+These methods work well for dynamic environment where the state of the market is contiously changing.
+For example, gradient ascent has been used for forex investing \citep{su142215328}.
+The gradient ascent algorithm is very similar to the gradient descent \citep{cauchy1847methode} algorithm commonly used in machine learning.
+The key differnce is that it seeks to maximize a function's value rather minimize it.
+Gradient ascent is used to maximize the expected revenue function, $R(p_i)$ with respect to price.
+It is defined as
+
+\begin{equation}
+	\mathbf{x}_{t+1} = \mathbf{x}_t + \eta \nabla f(\mathbf{x}_t)
+	\label{eq:grad}
+\end{equation}
+
+where $\mathbf{x}_t$ is the parameter vector at iteration $t$
+,$\mathbf{x}_{t+1}$ is the updated parameter vector,
+$\eta$ is the learning rate (step size)
+, and $\nabla f(\mathbf{x}_t)$ is the gradient of the objective function $f$ at point $\mathbf{x}_t$.
+
+Applying this to the revenue function, $R(p_i)$, we can get and update function for the price.
+The gradient of $R$ with respect to $p$ is
+$$\diffp{R}{p} = \mathbb{P}(w)(1 + \alpha p \cdot (\mathbb{P}(w) - 1))$$
+
+Using this with the gradient ascent algorithm Equation \ref{eq:grad}, the price update rule is
+
+\begin{equation}
+	p_{t+1} = p_t + \eta \diffp{R}{{p_t}}
+	\label{eq:optim_price}
+\end{equation}
+
+As all nodes continuly update their prices, they will converge on the price that gives
+maximum revenue for each node individually.
+
 \subsection{Network Equilibrium}
-
-\subsection{Strategy-Proofness}
 

### 2025-05-05 docs/paper/main.tex
cryptoeconomics

@@
 \begin{abstract}%   <- trailing '%' for backward compatibility of .sty file
+	This project explores a framework that enables distributed running of large language models across personal computing devices connected in a peer-to-peer network.
+	While current advanced AI models require substantial computing resources typically available only to large organizations,
+	P2P-LLM offers an alternative approach by dividing these models into smaller parts that can be processed across multiple personal computers.
+	The system includes efficient routing mechanisms to find optimal paths through the network, balancing computational speed and cost.
+	To encourage participation, the project develops a fair pricing system where participants are rewarded for contributing their computing power.
+	This marketplace is secured by blockchain technology, which handles payments and ensures that agreements between participants are honored.
+	The P2P-LLM approach demonstrates how collaborative computing could make advanced AI more accessible while enhancing privacy and user autonomy,
+	potentially transforming how these technologies are accessed in the future.
 \end{abstract}
@@
 As all nodes continuly update their prices, they will converge on the price that gives
-maximum revenue for each node individually.
+maximum revenue for each node individually. Once this happens the network will be in a steady state where
+no node will change its price.
 
@@
 
+When all nodes are at the state of equilibrium, each layer is at a Nash-Equilibrium (NE), meaning that any deviation in price
+will result is a a lower expected revenue. Formally this is defined as the utility of the optimal stategy being greater than or equal to any single deviation.
+In the P2P-LLM network, the utility is just the revenue function $R$.
+A price profile $p^*$ for a layer is a NE when
+
+\begin{equation}
+	u_i(p_i^*, p^*_{-i}) \geq u_i(p_i, p^*_{-i}) \forall p_i \in \mathbb{R}
+\end{equation}
+
+This is a equilibrium for an individual layer in the network, but the whole network may
+not at equilibrium. If the peers in the network are not evenly distributed,
+some layers may have less peers serving them, which will lead to inefficiencies.
+Ideally the computational power in the network will be evenly split between all layers
+in the LLM. This will lead to some nodes benefiting by changing which layers to serve.
+
+The optimal layer for a given node is the one in which they will have the largest
+share of computation. The percentage of computation a node has can by normalizing the
+computational cost across a layer. A reciprocal norm is used to find the share of computational power in the layer.
+It is defined as
+
+\begin{equation}
+	s_l(c_i) = \frac{c_i^{-1}}{\sum_{j=i}^{n_l}c_j^{-1}}
+	\label{eq:norm}
+\end{equation}
+
+where $l$ is the layer, $n_l$ is the number of nodes serving the layer $l$, and $c_i$ is the computational cost.
+The optimal layer for a node, is the one that maximizes this value.
+
+\begin{equation}
+	l^* = \text{max}_l s_l(c_i)
+	\label{eq:max}
+\end{equation}
+
+In the P2P-LLM network, peers will periodically change layers if they are already not in the optimal state.
+Changing layers will increase the peers expected revenue while also increasing the throughput of the network overall.
+In this case the incentives of the individual nodes are aligned with the whole network overall.
+When no peers have a useful change then the network is in an efficient state.
+
 \section{Cryptoeconomics}
+The P2P-LLM network requires a secure, transparent, and decentralized mechanism to facilitate transactions between peers.
+The blockchain provides a secure and decentralized way to allow peers to form contracts with eachother
+and exchange payment in cryto-currencies for computation.
+Cryptoeconomics has proven to be successful in the past with some application being in
+resources trading through the blockchain. Specifically, research has been done to enable peer-to-peer surplus energy on the blockchain \citep{WONGTHONGTHAM2021107299}.
+For the P2P-LLM network, the blockchain serves three primary functions: (1) recording the state of the network including available nodes and their capabilities, (2) facilitating secure payments between peers, and (3) executing smart contracts that govern computational resource sharing.
 
@@
 
+Blockchain technology provides an ideal foundation for this system, as it offers immutability, transparency, and security without relying on a central authority.
+
+The blockchain implementation for P2P-LLM employs a Proof-of-Stake (PoS) consensus mechanism rather than the energy-intensive Proof-of-Work (PoW) used in systems like Bitcoin \citep{nakamoto2008bitcoin}.
+This design choice aligns with our goal of resource efficiency, as PoS validators are selected based on the quantity of tokens they have staked, consuming significantly less energy than PoW mining operations \citep{saleh2021blockchain}.
+This approach is particularly appropriate for a system focused on computational resource optimization.
+
+Each block in the P2P-LLM blockchain contains transactions representing computational resource exchanges between peers.
+These transactions include metadata such as the identity of the participating nodes, the layers being computed, the computational cost, and the agreed-upon price.
+Additionally, the blockchain maintains a distributed registry of all active nodes and their capabilities ($\ell_i$, $c_i$, $p_i$), which is critical for the path-finding algorithm described in Section 3.1.
+
+To ensure scalability, the P2P-LLM blockchain implements a sharding mechanism that partitions the network state by model layers.
+This design allows transactions related to specific model layers to be processed in parallel, significantly increasing throughput as the network grows.
+Each shard maintains its own state and processes transactions independently, with periodic cross-shard communication to maintain overall network consistency \citep{yu2020survey}.
+
 \subsection{Contracts}
+
+Smart contracts form the backbone of the interaction mechanism in the P2P-LLM network.
+These self-executing contracts with the terms of agreement directly written into code automate the negotiation, execution, and settlement processes between peers without requiring trust or intermediaries.
+
+In the P2P-LLM network, three types of smart contracts are employed:
+
+\begin{enumerate}
+	\item \textbf{Registration Contracts}: These contracts handle the onboarding of new nodes to the network.
+When a node joins, it executes a registration contract that records its capabilities ($\ell_i$, $c_i$, $p_i$) on the blockchain.
+This contract also requires the node to stake a minimum amount of tokens as collateral, which can be forfeited if the node behaves maliciously or fails to deliver promised computational resources.
+	\item \textbf{Service Level Agreements (SLAs)}: These contracts formalize the terms of computational resource sharing between peers.
+An SLA contract specifies the model layers to be computed, the expected computational performance (in terms of latency and throughput), the price per computation, and penalties for non-compliance.
+The contract is automatically executed when a peer requests computation, with payment held in escrow until the computation is successfully completed and verified.
+	\item \textbf{Payment Channels}: To minimize transaction costs and latency, the P2P-LLM network implements payment channels similar to Bitcoin's Lightning Network \citep{poon2016bitcoin}.
+These channels allow peers to conduct multiple transactions off-chain, only settling the final balance on the blockchain when the channel is closed.
+This approach is particularly valuable for high-frequency, low-value transactions that are common in LLM inference operations.
+\end{enumerate}
+
+The execution of these contracts is governed by a verification mechanism that ensures computational integrity.
+When a node performs computation for another peer, the input, output, and intermediate states are cryptographically hashed and recorded on the blockchain.
+This creates a verifiable proof of computation that can be used to resolve disputes and ensure that nodes are correctly performing their assigned tasks.
+
+To optimize contract execution in the dynamic environment of the P2P-LLM network, we implement an adaptive pricing mechanism based on the concepts described in Section 3.3.
+This mechanism allows for continuous adjustment of prices based on network conditions, ensuring that nodes are appropriately incentivized to provide computational resources where they are most needed.
+
+The combination of these contract mechanisms creates a self-regulating marketplace for computational resources that aligns individual incentives with the overall efficiency of the network.
+Nodes are rewarded for providing reliable, cost-effective computation, while clients can access LLM capabilities at competitive prices without relying on centralized service providers.
 
@@
 % needed in general before appendices/bibliography.
-
+%
 \newpage
@@
 
+\newpage
+
 \section{Shortest Path}

### 2025-05-05 docs/paper/main.tex
fix typos

@@
 The idea of pooling compute power from many computers to form a distributed supercomputer is not new. This concept of Crowd Computing
-has been used ever since large networks of computer were formed. The predominant use of this method is to fascilitate academic research.
+has been used ever since large networks of computer were formed. The predominant use of this method is to facilitate academic research.
 Researchers publish problem that that are working on, and anyone can help contribute by volunteering to donate computing power.
@@
 
-LLM inference is a perfect candidate for P2P network because it has technical requirments that prohibit most personal computers from being able to run
-large models with billions of parameters, and it can easilly be split into small chunks that can be run on several computers at the same time.
+LLM inference is a perfect candidate for P2P network because it has technical requirements that prohibit most personal computers from being able to run
+large models with billions of parameters, and it can easily be split into small chunks that can be run on several computers at the same time.
 BitWorker \citep{Durand_Gasparyan_Rouvinez_Aad_Braun_Trinh_2015} is a protocol designed to compute any parallel computing task across a peer-to-peer network.
@@
 in the network is capable of serving one or multiple of these blocks. In order to run an inference step, a client will find a optimal path of servers
-in the network thats forms the complete model and minimizes time required. In my work I explore a similar approach with a network of distributed computers that serve a specific part of the whole LLM,
+in the network that forms the complete model and minimizes time required. In my work I explore a similar approach with a network of distributed computers that serve a specific part of the whole LLM,
 but I expand upon this and add incentive mechanisms that reward nodes for donating their computational power.
-This incentive mechanism also fucilitates optimal allocation of nodes to maximize throughput, by each
+This incentive mechanism also facilitates optimal allocation of nodes to maximize throughput, by each
 node maximizing expected revenue individually.
@@
 Fundamentally, a peer-to-peer network is a decentralized system where each devices acts as a client and a sever.
-Each devices can send and recieve data which eliminates the need for a centralized server. The central benefit of a P2P network
-is that recources are pooled and shared between peers, so the combined resources available to an individual peer is greater than that nodes own resources.
+Each devices can send and receive data which eliminates the need for a centralized server. The central benefit of a P2P network
+is that resources are pooled and shared between peers, so the combined resources available to an individual peer is greater than that nodes own resources.
 A peer-to-peer network can be built to share any type of resource. In the case of BitTorrent, bandwidth and files are shared between peers.
-For the case of LLM inference, peers will need to ba able to share bandwidth, data, and computational power.
+For the case of LLM inference, peers will need to be able to share bandwidth, data, and computational power.
 
-A peer-to-peer network is defined as having $n$ nodes in the network. There is an LLM model with $m$ total layers which will be devided between nodes.
+A peer-to-peer network is defined as having $n$ nodes in the network. There is an LLM model with $m$ total layers which will be divided between nodes.
 Each node $N$ in the network is a tuple $N(\ell, l, c, p)$ where
@@
 	\item $l_{ij} \in \mathbb{R}$ is the network latency between nodes $i$ and $j$,
-	\item $c_i \in \mathbb{R}$ is the computational cost of the node, measured in miliseconds
+	\item $c_i \in \mathbb{R}$ is the computational cost of the node, measured in milliseconds
 	\item $p_i \in \mathbb{R}$ is the price the nodes charges for its compute.
@@
 
-In order to use the network to run the LLM, a node must first find a sequence of nodes in the graph that form a complete model.
-Because the LLM layers must be computed sequentially, the node must find a path through the network that will ideally compute
+In order to use the network to run the LLM, a peer must first find a sequence of nodes in the graph that form a complete model.
+Because the LLM layers must be computed sequentially, the peer must find a path through the network that will ideally compute
 the LLM in the least amount of time possible and at the lowest price. This problem can be solved by viewing the network as a directed graph where weights correspond
-to the computational cost of nodes. The edges of the graph correspond the compatability between the layers that each node in serving.
-Specifically, every node is connected to all nodes that are serving the consecutive layer of the model. A vizualization of this directed graph is shown in Figure \ref{fig:layered_graph}.
+to the computational cost of nodes. The edges of the graph correspond the compatibility between the layers that each node in serving.
+Specifically, every node is connected to all nodes that are serving the consecutive layer of the model. A visualization of this directed graph is shown in Figure \ref{fig:layered_graph}.
 
@@
 
-Due to this property, the P2P network graph is a directed acyclical graph (DAG). This means that there are efficient
+Due to this property, the P2P network graph is a directed acyclic graph (DAG). This means that there are efficient
 algorithms to find the shortest path between two nodes. The first step is to perform a topological sort on the nodes in the network.
 This is an ordering of the nodes such that all neighbors of a node come after the node in the ordering.
-For any graph $G = (V, E)$ a totological ordering is an order $\prec$ on $V$ such that if $(u \rightarrow v) \in E$ then $u \prec v$.
+For any graph $G = (V, E)$ a topological ordering is an order $\prec$ on $V$ such that if $(u \rightarrow v) \in E$ then $u \prec v$.
 For example, a topological ordering of the DAG in Figure \ref{fig:layered_graph} is $[0,1,2,3,4,5,6,7,8]$.
@@
 
-\subsection{Pareto Effeciency}
+\subsection{Pareto Efficiency}
 
 The optimal path is well defined when weights for nodes are clearly defined, but there is not a clear way to define
-weights for nodes in this case. In the P2P-LLM network there are two competing criterea that define the weight of node: computational cost and price.
+weights for nodes in this case. In the P2P-LLM network there are two competing criterion that define the weight of node: computational cost and price.
 The algorithm described above uses a single objective (SO), while the optimal path in the network is a multi-objective (MO) optimization problem.
@@
 since the shortest path algorithm is designed for SO objective, it is the most practical solution for this task. In order to reframe the problem as a single objective,
-a weighed aggreagte of the objetives is used. In the case for the peer-to-peer network, the SO is a weighed sum of computational cost $c_i$ and price $p_i$.
+a weighed aggregate of the objectives is used. In the case for the peer-to-peer network, the SO is a weighed sum of computational cost $c_i$ and price $p_i$.
 The objective, or weight, of a node, $w_i$ is defined as.
@@
 
-However, this assumes that the weight $\alpha$ is known a priori. In general, there are many equivilent optimal solutions in a MO optimzation problem.
+However, this assumes that the weight $\alpha$ is known a priori. In general, there are many equivalent optimal solutions in a MO optimization problem.
 These are known and Pareto-optimal solutions. They are solutions such that there is no way to improve one objective without degrading any other objectives.
@@
 
-The set of all Pareto-optimal solutions forms a frontier (Figure \ref{fig:Pareto-optimal}) of equivilent solutions, but there is not a clear choice on which one should be used.
-In the case of the SO weighted aggreagte used in the P2P-LLM network, the parameter $\alpha$ decides where on the Pareto frontier the optimal solution lies.
+The set of all Pareto-optimal solutions forms a frontier (Figure \ref{fig:Pareto-optimal}) of equivalent solutions, but there is not a clear choice on which one should be used.
+In the case of the SO weighted aggregate used in the P2P-LLM network, the parameter $\alpha$ decides where on the Pareto frontier the optimal solution lies.
 Due to this, each node can independently decide that importance of price and computational cost in the optimal path through the network.
@@
 Each peer additionally has to choose a price to charge for other peers to use their computation.
-Ideally each node will act in its self-iterest and choose the price that maximizes revenue.
-If the price is too high, peers will choose equivlent node serving the same layers,
+Ideally each node will act in its self-interest and choose the price that maximizes revenue.
+If the price is too high, peers will choose equivalent node serving the same layers,
 while if the price is too low, the total revenue will be less than ideal.
@@
 If we can define a revenue function based on these parameters, then the optimal price can be found by maximizing this function with respect to $p_i$.
-The revenue a node recieves for a single peer using the network would be its price multiplied by the probability of being chosen in the optimal path.
+The revenue a node receives for a single peer using the network would be its price multiplied by the probability of being chosen in the optimal path.
 
@@
 Using this method gives a smooth expected revenue function, and prices will reflect how much each nodes contributes to the network.
-Specifcally, if a nodes contributes more compute power to the network, demonstrated as a lower computational cost $c_i$, the optimal
+Specifically, if a nodes contributes more compute power to the network, demonstrated as a lower computational cost $c_i$, the optimal
 price they will charge will be higher, and they will be rewarded with a higher expected revenue.
-A vizualization of how $c_i$ effects the expected revenue curve is shown in Figure \ref{fig:exp_rev}.
+A visualization of how $c_i$ effects the expected revenue curve is shown in Figure \ref{fig:exp_rev}.
 
-Now with the expected revnue function, the optimal price can be found by finding the price that maximizes $R(p_i)$.
+Now with the expected revenue function, the optimal price can be found by finding the price that maximizes $R(p_i)$.
 Unfortunately, there is not a closed form solution to this problem, but there are methods that can be used.
-Iterative pricing mechanism \citep{ecf80b8b-07bb-374f-ab3f-2cc6a349f689} are used to find optimal prices by making iterative changes to the price until it converages at an optimal point.
-These methods work well for dynamic environment where the state of the market is contiously changing.
+Iterative pricing mechanism \citep{ecf80b8b-07bb-374f-ab3f-2cc6a349f689} are used to find optimal prices by making iterative changes to the price until it converges at an optimal point.
+These methods work well for dynamic environment where the state of the market is continuously changing.
 For example, gradient ascent has been used for forex investing \citep{su142215328}.
 The gradient ascent algorithm is very similar to the gradient descent \citep{cauchy1847methode} algorithm commonly used in machine learning.
-The key differnce is that it seeks to maximize a function's value rather minimize it.
+The key difference is that it seeks to maximize a function's value rather minimize it.
 Gradient ascent is used to maximize the expected revenue function, $R(p_i)$ with respect to price.
@@
 
-As all nodes continuly update their prices, they will converge on the price that gives
+As all nodes continually update their prices, they will converge on the price that gives
 maximum revenue for each node individually. Once this happens the network will be in a steady state where
@@
 When all nodes are at the state of equilibrium, each layer is at a Nash-Equilibrium (NE), meaning that any deviation in price
-will result is a a lower expected revenue. Formally this is defined as the utility of the optimal stategy being greater than or equal to any single deviation.
+will result in a lower expected revenue. Formally this is defined as the utility of the optimal strategy being greater than or equal to any single deviation.
 In the P2P-LLM network, the utility is just the revenue function $R$.

### 2025-05-05 docs/paper/main.tex
revising

@@
 Each devices can send and receive data which eliminates the need for a centralized server. The central benefit of a P2P network
-is that resources are pooled and shared between peers, so the combined resources available to an individual peer is greater than that nodes own resources.
+is that resources are pooled and shared between peers, so the combined resources available to an individual peer is greater than that peer's own resources.
 A peer-to-peer network can be built to share any type of resource. In the case of BitTorrent, bandwidth and files are shared between peers.
@@
 
-In order to use the network to run the LLM, a peer must first find a sequence of nodes in the graph that form a complete model.
+In order to use the network to run the LLM, a peer must first find a sequence of servers in the network that form a complete model.
 Because the LLM layers must be computed sequentially, the peer must find a path through the network that will ideally compute
-the LLM in the least amount of time possible and at the lowest price. This problem can be solved by viewing the network as a directed graph where weights correspond
-to the computational cost of nodes. The edges of the graph correspond the compatibility between the layers that each node in serving.
-Specifically, every node is connected to all nodes that are serving the consecutive layer of the model. A visualization of this directed graph is shown in Figure \ref{fig:layered_graph}.
+the LLM in the least amount of time possible and at the lowest price.
+This problem can be solved by viewing the network as a directed graph where nodes are peers serving the LLM lyaers and weights correspond
+to the computational cost and latency of nodes. The edges of the graph correspond to the compatibility between the layers that each node in serving.
+Specifically, every node is connected to every node that are serving the consecutive layer of the model. A visualization of this directed graph is shown in Figure \ref{fig:layered_graph}.
 
@@
 
-The optimal path is well defined when weights for nodes are clearly defined, but there is not a clear way to define
-weights for nodes in this case. In the P2P-LLM network there are two competing criterion that define the weight of node: computational cost and price.
+The optimal path is well defined when weights for nodes are clearly defined, but there is not an apparent way to define
+weights for nodes in this case. In the P2P-LLM network, there are two competing criterion that define the weight of node: computational cost and price.
 The algorithm described above uses a single objective (SO), while the optimal path in the network is a multi-objective (MO) optimization problem.
@@
 
-However, this assumes that the weight $\alpha$ is known a priori. In general, there are many equivalent optimal solutions in a MO optimization problem.
+However, this assumes that the parameter $\alpha$ is known a priori. In general, there are many equivalent optimal solutions in a MO optimization problem.
 These are known and Pareto-optimal solutions. They are solutions such that there is no way to improve one objective without degrading any other objectives.
@@
 In the case of the SO weighted aggregate used in the P2P-LLM network, the parameter $\alpha$ decides where on the Pareto frontier the optimal solution lies.
-Due to this, each node can independently decide that importance of price and computational cost in the optimal path through the network.
+Due to this, each node can independently decide the importance of price and computational cost in the optimal path through the network by choosing the parameter $\alpha$.
 
@@
 Each peer additionally has to choose a price to charge for other peers to use their computation.
-Ideally each node will act in its self-interest and choose the price that maximizes revenue.
-If the price is too high, peers will choose equivalent node serving the same layers,
+Logically, each node will act in its self-interest and choose the price that maximizes revenue.
+If the price is too high, peers will choose equivalent nodes serving the same layers,
 while if the price is too low, the total revenue will be less than ideal.
-The price they choose should reflect the current state of the network, and adapt to conditions.
+The price they choose should reflect the current state of the network, and adapt to changing conditions.
 In this context, price optimization become difficult as it is a dynamic environment
@@
 This can be exploited to narrow down the complexities of this problem.
-Working with this leads to the conclusion that a nodes price should be determined
+Working with this leads to the conclusion that a node's price should be determined
 by its own price and computational cost and the price and computational cost of all other peers serving the same layers.
@@
 These methods work well for dynamic environment where the state of the market is continuously changing.
-For example, gradient ascent has been used for forex investing \citep{su142215328}.
-The gradient ascent algorithm is very similar to the gradient descent \citep{cauchy1847methode} algorithm commonly used in machine learning.
+For example, gradient ascent has been used for forex investing with algorithmic trading \citep{su142215328}.
+The gradient ascent algorithm is very similar to the gradient descent algorithm \citep{cauchy1847methode} commonly used in machine learning.
 The key difference is that it seeks to maximize a function's value rather minimize it.
-Gradient ascent is used to maximize the expected revenue function, $R(p_i)$ with respect to price.
+Gradient ascent can be applied in the P2P-LLM network to maximize the expected revenue function, $R(p_i)$, with respect to price.
 It is defined as
@@
 
-Applying this to the revenue function, $R(p_i)$, we can get and update function for the price.
+Applying this to the revenue function, $R(p_i)$, we can get an update rule for the price.
 The gradient of $R$ with respect to $p$ is
@@
 
-Using this with the gradient ascent algorithm Equation \ref{eq:grad}, the price update rule is
+Using this with the gradient ascent algorithm (Equation \ref{eq:grad}), the price update rule is
 
@@
 maximum revenue for each node individually. Once this happens the network will be in a steady state where
-no node will change its price.
+no node will want to change its price.
 
@@
 
-When all nodes are at the state of equilibrium, each layer is at a Nash-Equilibrium (NE), meaning that any deviation in price
+When all nodes are at the state of equilibrium, each layer in the network is at a Nash-Equilibrium (NE), meaning that any deviation in price
 will result in a lower expected revenue. Formally this is defined as the utility of the optimal strategy being greater than or equal to any single deviation.
@@
 This is a equilibrium for an individual layer in the network, but the whole network may
-not at equilibrium. If the peers in the network are not evenly distributed,
+not be at equilibrium. If the peers in the network are not evenly distributed,
 some layers may have less peers serving them, which will lead to inefficiencies.
 Ideally the computational power in the network will be evenly split between all layers
-in the LLM. This will lead to some nodes benefiting by changing which layers to serve.
+in the LLM. In an unbalanced state, this will lead to some nodes benefiting by changing which layers of the LLM they serve.
 
 The optimal layer for a given node is the one in which they will have the largest
-share of computation. The percentage of computation a node has can by normalizing the
+share of computation. The percentage of computation a node has can be found by normalizing the
 computational cost across a layer. A reciprocal norm is used to find the share of computational power in the layer.
@@
 \begin{equation}
-	l^* = \text{max}_l s_l(c_i)
+	l^* = \text{max}_l \quad s_l(c_i)
 	\label{eq:max}
@@
 
-In the P2P-LLM network, peers will periodically change layers if they are already not in the optimal state.
+In the P2P-LLM network, peers will periodically change layers if they are not already in the optimal state.
 Changing layers will increase the peers expected revenue while also increasing the throughput of the network overall.
@@
 The blockchain implementation for P2P-LLM employs a Proof-of-Stake (PoS) consensus mechanism rather than the energy-intensive Proof-of-Work (PoW) used in systems like Bitcoin \citep{nakamoto2008bitcoin}.
-This design choice aligns with our goal of resource efficiency, as PoS validators are selected based on the quantity of tokens they have staked, consuming significantly less energy than PoW mining operations \citep{saleh2021blockchain}.
+This design choice aligns with the goal of resource efficiency, as PoS validators are selected based on the quantity of tokens they have staked, consuming significantly less energy than PoW mining operations \citep{saleh2021blockchain}.
 This approach is particularly appropriate for a system focused on computational resource optimization.
@@
 
-To optimize contract execution in the dynamic environment of the P2P-LLM network, we implement an adaptive pricing mechanism based on the concepts described in Section 3.3.
+To optimize contract execution in the dynamic environment of the P2P-LLM network, an adaptive pricing mechanism based on the concepts described in Section 3.3 is used.
 This mechanism allows for continuous adjustment of prices based on network conditions, ensuring that nodes are appropriately incentivized to provide computational resources where they are most needed.

### 2025-05-05 docs/paper/main.tex
results

@@
 \usepackage[thinc]{esdiff}
+\usepackage{multirow}
+\usepackage{array}
+\usepackage{tabularx}
+\usepackage{booktabs}
 
@@
 
+To evaluate the performance, stability, and efficiency of the propose P2P-LLM protocol, I implemented a simulated environment
+to model the dynamics of the network.
+The simulation explores the relationship between computational resource allocation, price optimization, and network equilibrium under various conditions without requiring the deployment of an actual LLM across distributed hardware.
+
+\subsection{Simulation Framework}
+The simulation framework implements a discrete event-based model of the P2P-LLM network, where each event corresponds to a peer action such as joining the network, processing requests, updating prices, or switching layers.
+The simulation progresses in timesteps, with each timestep representing a fixed duration (e.g., 1 second in simulated time).
+At each timestep, the following operations are performed:
+\begin{enumerate}
+	\item Process pending inference requests through the network
+	\item Update node prices according to the gradient ascent algorithm (Equation \ref{eq:optim_price})
+	\item Periodically, reallocate nodes to new layers (Equation \ref{eq:max})
+	\item Create new contracts for peers without a pending contract
+	\item Record metrics for analysis
+\end{enumerate}
+The simulation parameters can be configured to model various network sizes, LLM architectures, and peer behaviors, allowing for comprehensive sensitivity analysis.
+
+\subsection{Network Configuration}
+
+For the simulation, I chose to create a small network, with $n = 28$ total nodes, and a simulated LLM with $m = 4$ layers.
+The parameters of the nodes in the network were randomly initialized
+where $c_i \in (1,50)$, $l_i \in (1,20)$.
+All prices are intitially set at $1$.
+The inital state of the network not optimal with the peers being distributed between the $4$ layers in the configuration $[10, 4, 10, 4]$.
+For simplicity, all nodes have an $\alpha$ value of $0.5$ and the $\eta$ used in the iterative pricing function is $1$.
+
 \section{Results}
+
+\begin{table}[t]
+	\centering
+	\caption{P2P-LLM Network Metrics at Different Iteration Steps (Model with 4 Layers, 200 Peers)}
+	\label{tab:network-metrics}
+	\begin{tabular}{ccccccc}
+		\toprule
+		\textbf{Iteration} & \textbf{Metric} & \textbf{Layer 1} & \textbf{Layer 2} & \textbf{Layer 3} & \textbf{Layer 4} \\
+		\midrule
+		\multirow{3}{*}{0}
+		                   & Nodes           & 78               & 52               & 34               & 36               \\
+		                   & Avg. Price      & 5.42             & 5.28             & 5.87             & 5.31             \\
+		\midrule
+		\multirow{3}{*}{100}
+		                   & Nodes           & 62               & 48               & 43               & 47               \\
+		                   & Avg. Price      & 5.89             & 5.96             & 5.72             & 5.68             \\
+		\midrule
+		\multirow{3}{*}{500}
+		                   & Nodes           & 53               & 49               & 50               & 48               \\
+		                   & Avg. Price      & 6.12             & 6.08             & 6.10             & 6.05             \\
+		\midrule
+		\multirow{3}{*}{1000}
+		                   & Nodes           & 50               & 50               & 50               & 50               \\
+		                   & Avg. Price      & 6.14             & 6.15             & 6.13             & 6.15             \\
+		\midrule
+		\multirow{3}{*}{5000}
+		                   & Nodes           & 50               & 50               & 50               & 50               \\
+		                   & Avg. Price      & 6.13             & 6.14             & 6.14             & 6.13             \\
+		\bottomrule
+	\end{tabular}
+\end{table}
 

### 2025-05-05 docs/paper/main.tex
complete

@@
 \usepackage{lastpage}
-\jmlrheading{23}{2022}{1}{1/21}{9/22}{21-0000}{Author One and Author Two}
+%\jmlrheading{23}{2022}{1}{1/21}{9/22}{21-0000}{Author One and Author Two}
 
@@
 
-\begin{figure}
+\begin{figure}[ht]
 	\centering
@@
 		\begin{axis}[
-				width=12cm,
-				height=8cm,
+				width=10cm,
+				height=6cm,
 				xlabel={Computational Cost},
@@
 
-\begin{figure}
+If we can define a revenue function based on these parameters, then the optimal price can be found by maximizing this function with respect to $p_i$.
+The revenue a node receives for a single peer using the network would be its price multiplied by the probability of being chosen in the optimal path.
+
+\begin{equation}
+	R(p_i) = p_i \cdot \mathbb{P}(w_i)
+	\label{eq:revenue}
+\end{equation}
+
+The probability that a node is chosen is related to its weight (Equation \ref{eq:weight}).
+In order to get a distribution across all weights in the node's layer, the Boltzmann distribution \citep{boltzmann1868studien} can be used.
+This distribution give the probability that a system will be in certain state.
+
+\begin{equation}
+	\mathbb{P}(\epsilon_i) = \frac{e^{- \epsilon_i / kT}}{\sum_{j=1}^{M}e^{- \epsilon_j / kT}}
+	\label{eq:Boltzmann}
+\end{equation}
+
+where $\epsilon_i$ is the energy for state $i$, $k$ is the Boltzmann constant, and $T$ is the temperature of the system.
+For the purposes of the P2P-LLM network, $k$ and $T$ are dropped and $\epsilon_i$ is $w_i$ (Equation \ref{eq:weight}).
+Using this method gives a smooth expected revenue function, and prices will reflect how much each nodes contributes to the network.
+Specifically, if a nodes contributes more compute power to the network, demonstrated as a lower computational cost $c_i$, the optimal
+price they will charge will be higher, and they will be rewarded with a higher expected revenue.
+A visualization of how $c_i$ effects the expected revenue curve is shown in Figure \ref{fig:exp_rev}.
+
+\begin{figure}[h]
 	\centering
@@
 		\begin{axis}[
-				width=14cm,
-				height=8cm,
+				width=10cm,
+				height=6cm,
 				xlabel={$p_i$},
@@
 \end{figure}
-
-If we can define a revenue function based on these parameters, then the optimal price can be found by maximizing this function with respect to $p_i$.
-The revenue a node receives for a single peer using the network would be its price multiplied by the probability of being chosen in the optimal path.
-
-\begin{equation}
-	R(p_i) = p_i \cdot \mathbb{P}(w_i)
-	\label{eq:revenue}
-\end{equation}
-
-The probability that a node is chosen is related to its weight (Equation \ref{eq:weight}).
-In order to get a distribution across all weights in the node's layer, the Boltzmann distribution \citep{boltzmann1868studien} can be used.
-This distribution give the probability that a system will be in certain state.
-
-\begin{equation}
-	\mathbb{P}(\epsilon_i) = \frac{e^{- \epsilon_i / kT}}{\sum_{j=1}^{M}e^{- \epsilon_j / kT}}
-	\label{eq:Boltzmann}
-\end{equation}
-
-where $\epsilon_i$ is the energy for state $i$, $k$ is the Boltzmann constant, and $T$ is the temperature of the system.
-For the purposes of the P2P-LLM network, $k$ and $T$ are dropped and $\epsilon_i$ is $w_i$ (Equation \ref{eq:weight}).
-Using this method gives a smooth expected revenue function, and prices will reflect how much each nodes contributes to the network.
-Specifically, if a nodes contributes more compute power to the network, demonstrated as a lower computational cost $c_i$, the optimal
-price they will charge will be higher, and they will be rewarded with a higher expected revenue.
-A visualization of how $c_i$ effects the expected revenue curve is shown in Figure \ref{fig:exp_rev}.
 
@@
 	\item Create new contracts for peers without a pending contract
-	\item Record metrics for analysis
 \end{enumerate}
@@
 
-\begin{table}[t]
+\begin{table}[h]
 	\centering
-	\caption{P2P-LLM Network Metrics at Different Iteration Steps (Model with 4 Layers, 200 Peers)}
+	\caption{P2P-LLM Network Metrics at Different Iteration Steps (Model with 4 Layers, 28 Peers)}
 	\label{tab:network-metrics}
@@
 		\multirow{3}{*}{0}
-		                   & Nodes           & 78               & 52               & 34               & 36               \\
-		                   & Avg. Price      & 5.42             & 5.28             & 5.87             & 5.31             \\
+		                   & Nodes           & 10               & 4                & 10               & 4                \\
+		                   & Avg. Price      & 1                & 1                & 1                & 1                \\
 		\midrule
 		\multirow{3}{*}{100}
-		                   & Nodes           & 62               & 48               & 43               & 47               \\
-		                   & Avg. Price      & 5.89             & 5.96             & 5.72             & 5.68             \\
+		                   & Nodes           & 7                & 6                & 10               & 5                \\
+		                   & Avg. Price      & 1.92             & 2.20             & 1.80             & 2.31             \\
 		\midrule
 		\multirow{3}{*}{500}
-		                   & Nodes           & 53               & 49               & 50               & 48               \\
-		                   & Avg. Price      & 6.12             & 6.08             & 6.10             & 6.05             \\
+		                   & Nodes           & 7                & 6                & 8                & 7                \\
+		                   & Avg. Price      & 2.33             & 2.40             & 2.29             & 2.33             \\
 		\midrule
 		\multirow{3}{*}{1000}
-		                   & Nodes           & 50               & 50               & 50               & 50               \\
-		                   & Avg. Price      & 6.14             & 6.15             & 6.13             & 6.15             \\
-		\midrule
-		\multirow{3}{*}{5000}
-		                   & Nodes           & 50               & 50               & 50               & 50               \\
-		                   & Avg. Price      & 6.13             & 6.14             & 6.14             & 6.13             \\
+		                   & Nodes           & 7                & 7                & 7                & 7                \\
+		                   & Avg. Price      & 2.33             & 2.34             & 2.33             & 2.33             \\
 		\bottomrule
@@
 \end{table}
+
+When running the simulated environment, the behavior of the peers aligns with what is expected based on the theory described above.
+The starting state of the network has uniform pricing across all nodes, and there is a high concentration of peers in the first and third layers of the LLM.
+As the network progresses toward a state of equilibirum, the prices are expected to rise to meet the demand of the network, and reach a maximum where the expected revenue for the reective node is highest.
+Nodes are also expected to change the layer of the LLM they serve based on the location of other nodes in the network. Ideally, the nodes will be evenly distriubted between layers in the network.
+Looking at Table \ref{tab:network-metrics}, the expected actions occurs as the iteration of the simulation increases.
+It eventually reached a point of equilibrium where the prices and layers are constant.
 

### 2025-05-05 docs/paper/main.tex
move figures

@@
 \subsection{Pareto Efficiency}
-
-The optimal path is well defined when weights for nodes are clearly defined, but there is not an apparent way to define
-weights for nodes in this case. In the P2P-LLM network, there are two competing criterion that define the weight of node: computational cost and price.
-The algorithm described above uses a single objective (SO), while the optimal path in the network is a multi-objective (MO) optimization problem.
-There are several way to find optimal solutions to MO optimization problems \citep{1599245}. The simplest way is to convert it to a SO optimization problem, and
-since the shortest path algorithm is designed for SO objective, it is the most practical solution for this task. In order to reframe the problem as a single objective,
-a weighed aggregate of the objectives is used. In the case for the peer-to-peer network, the SO is a weighed sum of computational cost $c_i$ and price $p_i$.
-The objective, or weight, of a node, $w_i$ is defined as.
-
-\begin{equation}
-	w_i = \alpha \cdot p_i + (1 - \alpha) \cdot c_i
-	\label{eq:weight}
-\end{equation}
-
-\begin{figure}[ht]
+\begin{figure}[h]
 	\centering
@@
 \end{figure}
+The optimal path is well defined when weights for nodes are clearly defined, but there is not an apparent way to define
+weights for nodes in this case. In the P2P-LLM network, there are two competing criterion that define the weight of node: computational cost and price.
+The algorithm described above uses a single objective (SO), while the optimal path in the network is a multi-objective (MO) optimization problem.
+There are several way to find optimal solutions to MO optimization problems \citep{1599245}. The simplest way is to convert it to a SO optimization problem, and
+since the shortest path algorithm is designed for SO objective, it is the most practical solution for this task. In order to reframe the problem as a single objective,
+a weighed aggregate of the objectives is used. In the case for the peer-to-peer network, the SO is a weighed sum of computational cost $c_i$ and price $p_i$.
+The objective, or weight, of a node, $w_i$ is defined as.
+
+\begin{equation}
+	w_i = \alpha \cdot p_i + (1 - \alpha) \cdot c_i
+	\label{eq:weight}
+\end{equation}
 

### 2025-05-05 docs/paper/main.tex
final

@@
 thereby democratizing access to advanced artificial intelligence capabilities.
-\section{Realted Work}
+\section{Related Work}
 
@@
 has been used ever since large networks of computer were formed. The predominant use of this method is to facilitate academic research.
-Researchers publish problem that that are working on, and anyone can help contribute by volunteering to donate computing power.
+Researchers publish problem that that they are working on, and anyone can help contribute by donating their computing power.
 Projects that have successfully used crowd computing include SETI@Home \citep{10.1145/581571.581573} and Einstein@Home \citep{Steltner_2021}.
-This approach has proven to be successful in the past, but it has become less popular as the computational power of computers increased and access to supercomputers increased.
+This approach has proven to be successful in the past, but it has become less popular as the computational power of computers and access to supercomputers has increased.
 However, the use of idle compute power still has untapped applications, and the principles from crowd computing can be applied to modern tasks like LLM inference.
@@
 Clients send requests that will be processed by the servers on the network.
-The model is split into multiple sequential blocks of layers, and each server
+The model is split into multiple sequential blocks of the LLM's layers, and each server
 in the network is capable of serving one or multiple of these blocks. In order to run an inference step, a client will find a optimal path of servers
-in the network that forms the complete model and minimizes time required. In my work I explore a similar approach with a network of distributed computers that serve a specific part of the whole LLM,
+in the network that forms the complete model and minimizes the time required to compute the LLM.
+In my work, I explore a similar approach with a network of distributed computers that serve a specific part of the LLM,
 but I expand upon this and add incentive mechanisms that reward nodes for donating their computational power.
@@
 
-Fundamentally, a peer-to-peer network is a decentralized system where each devices acts as a client and a sever.
+Fundamentally, a peer-to-peer network is a decentralized system where each devices acts as a client and a server.
 Each devices can send and receive data which eliminates the need for a centralized server. The central benefit of a P2P network
@@
 the LLM in the least amount of time possible and at the lowest price.
-This problem can be solved by viewing the network as a directed graph where nodes are peers serving the LLM lyaers and weights correspond
+This problem can be solved by viewing the network as a directed graph where nodes are peers serving the LLM layers and weights correspond
 to the computational cost and latency of nodes. The edges of the graph correspond to the compatibility between the layers that each node in serving.
-Specifically, every node is connected to every node that are serving the consecutive layer of the model. A visualization of this directed graph is shown in Figure \ref{fig:layered_graph}.
+Specifically, each node is connected to every node that is serving the consecutive layer of the model. A visualization of this directed graph is shown in Figure \ref{fig:layered_graph}.
 
@@
 For example, a topological ordering of the DAG in Figure \ref{fig:layered_graph} is $[0,1,2,3,4,5,6,7,8]$.
-The algorithm for topological sort is shown in Appendix \ref{app:topo_sort}. With the topological order, dynamic programming can be used to find the shortest path in the network.
+The complete algorithm for topological sort is shown in Appendix \ref{app:topo_sort}. With the topological order, dynamic programming can be used to find the shortest path in the network.
 This algorithm will iterate over the ordering, and search all the node's neighbors for the one with the lowest weight.
@@
 There are several way to find optimal solutions to MO optimization problems \citep{1599245}. The simplest way is to convert it to a SO optimization problem, and
-since the shortest path algorithm is designed for SO objective, it is the most practical solution for this task. In order to reframe the problem as a single objective,
-a weighed aggregate of the objectives is used. In the case for the peer-to-peer network, the SO is a weighed sum of computational cost $c_i$ and price $p_i$.
-The objective, or weight, of a node, $w_i$ is defined as.
+since the shortest path algorithm is designed for a single objective, it is the most practical solution for this task. In order to reframe the problem as a single objective,
+a weighed aggregate of the multiple objectives is used. In the case of the peer-to-peer network, the SO is a weighed sum of computational cost $c_i$ and price $p_i$.
+The objective, or weight, of a node $w_i$ is defined as.
 
@@
 However, this assumes that the parameter $\alpha$ is known a priori. In general, there are many equivalent optimal solutions in a MO optimization problem.
-These are known and Pareto-optimal solutions. They are solutions such that there is no way to improve one objective without degrading any other objectives.
+These are known as Pareto-optimal solutions. They are solutions such that there is no way to improve one objective without degrading any other objectives.
 A solution is said to be Pareto-optimal if there are no other solutions that dominate it. A solution $x_1$ dominates $x_2$ if
@@
 The gradient ascent algorithm is very similar to the gradient descent algorithm \citep{cauchy1847methode} commonly used in machine learning.
-The key difference is that it seeks to maximize a function's value rather minimize it.
+The key difference is that it seeks to maximize a function's value rather than minimize it.
 Gradient ascent can be applied in the P2P-LLM network to maximize the expected revenue function, $R(p_i)$, with respect to price.
@@
 
-where $\mathbf{x}_t$ is the parameter vector at iteration $t$
-,$\mathbf{x}_{t+1}$ is the updated parameter vector,
-$\eta$ is the learning rate (step size)
-, and $\nabla f(\mathbf{x}_t)$ is the gradient of the objective function $f$ at point $\mathbf{x}_t$.
+where $\mathbf{x}_t$ is the parameter vector at iteration $t$,
+$\mathbf{x}_{t+1}$ is the updated parameter vector,
+$\eta$ is the learning rate (step size),
+and $\nabla f(\mathbf{x}_t)$ is the gradient of the objective function $f$ at point $\mathbf{x}_t$.
 
@@
 
-Using this with the gradient ascent algorithm (Equation \ref{eq:grad}), the price update rule is
+Using this with the gradient ascent algorithm (Equation \ref{eq:grad}), the price update rule becomes
 
@@
 Cryptoeconomics has proven to be successful in the past with some application being in
-resources trading through the blockchain. Specifically, research has been done to enable peer-to-peer surplus energy on the blockchain \citep{WONGTHONGTHAM2021107299}.
+resources trading through the blockchain. Specifically, research has been done to enable peer-to-peer surplus energy trading on the blockchain \citep{WONGTHONGTHAM2021107299}.
 For the P2P-LLM network, the blockchain serves three primary functions: (1) recording the state of the network including available nodes and their capabilities, (2) facilitating secure payments between peers, and (3) executing smart contracts that govern computational resource sharing.
@@
 where $c_i \in (1,50)$, $l_i \in (1,20)$.
-All prices are intitially set at $1$.
-The inital state of the network not optimal with the peers being distributed between the $4$ layers in the configuration $[10, 4, 10, 4]$.
-For simplicity, all nodes have an $\alpha$ value of $0.5$ and the $\eta$ used in the iterative pricing function is $1$.
+All prices are initially set at $1$.
+The initial state of the network is not optimal with the peers being distributed between the $4$ layers in the configuration $[10, 4, 10, 4]$.
+For simplicity, all nodes have an $\alpha$ value in Equation \ref{eq:weight} of $0.5$ and the $\eta$ used in the iterative pricing function (Equation \ref{eq:optim_price}) is $1$.
 
@@
 The starting state of the network has uniform pricing across all nodes, and there is a high concentration of peers in the first and third layers of the LLM.
-As the network progresses toward a state of equilibirum, the prices are expected to rise to meet the demand of the network, and reach a maximum where the expected revenue for the reective node is highest.
-Nodes are also expected to change the layer of the LLM they serve based on the location of other nodes in the network. Ideally, the nodes will be evenly distriubted between layers in the network.
+As the network progresses toward a state of equilibrium, the prices are expected to rise to meet the demand of the network, and reach a maximum where the expected revenue for the respective node is highest.
+Nodes are also expected to change the layer of the LLM they serve based on the location of other nodes in the network. Ideally, the nodes will be evenly distributed between layers in the network.
 Looking at Table \ref{tab:network-metrics}, the expected actions occurs as the iteration of the simulation increases.
